---
title: "Cash Plus, Safety Plus? Intimate Partner Violence and Economic Inclusion in Mauritania"
subtitle: "Empirical strategy & Results"
author: "IBRAHIM KASSOUM Habibou"
date: '`r format(Sys.Date(), "%d %B %Y")`'
output: 
  officedown::rdocx_document:
    mapstyles:
      Normal: ['First Paragraph']
    number_sections: true
    fig_caption: true
---



```{r setup, include=FALSE}
# Set random seed for reproducibility
set.seed(7654)

# Set number of decimal places to display
options(digits = 3)

# Configure knitr chunk options:
knitr::opts_chunk$set(
 screenshot.force = TRUE,           # turn HTML widgets into PNGs
 echo = FALSE,          # Don't show R code in output
 message = FALSE,       # Don't show messages
 warning = FALSE,       # Don't show warnings
 cache = FALSE,         # Don't cache results
 fig.align = 'center',  # Center figures
 fig.width = 6,         # Figure width in inches
 fig.asp = 0.618,       # Figure aspect ratio (golden ratio)
 fig.show = "hold",      # Hold multiple plots until end of chunk
 screenshot.opts = list(vwidth = 1200, vheight = 800, delay = 0.2)
)


# Set dplyr print options to show 6 rows max
options(dplyr.print_min = 6, dplyr.print_max = 6)

```


```{r, include=FALSE, results='hide', echo=FALSE}

######################## Importing library and external files ##################
### List of required packages
required_packages <- c("tidyverse", "dplyr","officedown", "officer", "gtsummary",
                       "stargazer", "lfe","labelled","car","broom","purrr",
                       "flextable","kableExtra")

### Check if packages are installed
missing_packages <- setdiff(required_packages, installed.packages()[,"Package"])

### Install missing packages
if (length(missing_packages) > 0) {
  install.packages(missing_packages)
}

### Load all packages
lapply(required_packages, library, character.only = TRUE)

# Remove all objects
rm(list = ls())

# Source functions from external file
source("functions.R")
```


```{r echo=F}

set_gtsummary_theme(theme_gtsummary_compact())

######### Create default BioAVR table from dataframe
#
# Dependencies : dplyr, flextable, officer
# source link : https://www.r-bloggers.com/2021/11/publication-ready-tables-with-flextable-and-own-theme-in-r/
customtab_defaults <- function(){
set_flextable_defaults(font.family = "Times New Roman",
font.size = 10,
border.color = "black")
}

custom_tab <- function(df, header, footer){
flextable(df) %>%
add_header_lines(header) %>%
add_footer_lines(footer) %>%
bold(i = 1, part = "header") %>%
hline_top(part = "header",
border = fp_border(color = "white",
width = 3,
style = "solid")) %>%
hline(i = 1,
part = "header",
border = fp_border(color = "black",
width = 0.25,
style = "solid")) %>%
hline_top(part = "body",
border = fp_border(color = "black",
width = 0.25,
style = "solid")) %>%
hline_bottom(part = "body",
border = fp_border(color = "black",
width = 0.25,
style = "solid")) %>%
hline_bottom(part = "footer",
border = fp_border(color = "black",
width = 0.25,
style = "solid")) %>%
border_inner_h(part = "body",
border = fp_border(color = "black",
width = 0.25,
style = "dotted")) %>%
autofit(part = "body") %>%
bg(part = "body", bg = "white") %>%
align(part = "all", align = "center") %>%
align(j = 1, part = "all", align = "left")
}


```


```{r}

######################## Loading the datasets ##################################
# Read the file containing the global dataframe into followup_ipv_MRT_hh

followup_ipv_MRT_hh <- readRDS(paste0(getwd(),"/output/data/followup_ipv_MRT_hh.rds"))


followup_ipv_MRT_hh$treatment_pi <- haven::as_factor(followup_ipv_MRT_hh$treatment_pi)
# Convert cash transfer treatment to factor
followup_ipv_MRT_hh$treatment_csh_trnsfr <- haven::as_factor(followup_ipv_MRT_hh$treatment_csh_trnsfr)

```

<!---BLOCK_TOC--->




<!---BLOCK_LANDSCAPE_START--->
\newpage
# Summary


**Overall Effects**

* Most coefficients across all intervention types and IPV measures are statistically non-significant, suggesting that the interventions generally had limited measurable impact on reducing intimate partner violence.
* For some types of violence, especially physical violence and sexual violence, the baseline prevalence is quite low (approximately 1 percent and 4.5 percent respectively), which creates a "floor effect" making detection of significant effects statistically challenging.
* Comparisons between treatment arms (Full vs. Psychosocial, Full vs. Capital, Psychosocial vs. Capital) revealed no statistically significant differences, indicating no clear advantage of one intervention approach over others.


**Heterogeneity Analysis Findings**

The heterogeneity analysis revealed several important differential effects:

* Partner-Controlling Behavior: the Tekavoul cash transfer program increased the risk of partner-controlling behavior specifically for female-headed households. Conversely, partner-controlling behavior decreased for beneficiaries of the Economic inclusion program among women with above-median baseline control over household resources.

* Emotional Violence: the Economic inclusion program slightly increased the risk of emotional violence for women with low baseline control over household resources, while showing no significant effects for women with high control. Emotional violence increased among Tekavoul program beneficiaries with above-median years of education compared to the control group.

* Physical Violence: no significant effects were detected on physical violence risk, likely due to the low baseline prevalence limiting statistical power.

* Sexual Violence: sexual violence decreased for recipients of the capital and full packages with the highest share of resources owned by their partner. Sexual violence increased for Tekavoul program beneficiaries with above-median years of education compared to the control group.

* Economic Violence: the full package slightly increased the risk of economic violence for Economic inclusion program beneficiaries with low baseline control over household resources.

* Other IPV Indicators: little to no effect was found on other IPV indicators across the intervention groups.

\newpage

# Empirical strategy 

**Economic inclusion Program**

We are interested in measuring the causal effect of the Economic inclusion on IPV risk at the second follow up survey, which is three years after the start of the intervention. In our base estimation, we take into account the study design and control for the level of stratification by estimating the following model:


$$
Y_{ic} = \beta_0 + \beta_1 Capital_{c} + \beta_2 Psychosocial_{c} + \beta_3 Full_{c} + \beta_4 SP_{c} + \delta_{i} + \epsilon_{i} (1)
$$

$Y_{ic}$ is the IPV outcome of interest for woman *i* from cluster *c* at the second follow up survey, and $SP_{c}$ is a control for the social promotion space which is the level of stratification. $Capital_{c}$, $Phychosocial_{c}$ and $Full_{c}$ are indicators for the treatment group of the cluster *c*. We also include enumerator fixed effect $\delta_{i}$ to control for potential biases that might arise from differences in enumerators characteristics or how they conduct interviews and build rapport with respondents. This is particularly important when measuring sensitive outcomes such as IPV, as reports can vary depending on the interviewer's approach to the respondent. The error term $\epsilon_{i}$ captures unobserved factors affecting IPV outcomes. 
The coefficients $\beta_1$, $\beta_2$ and $\beta_3$ represent the intent-to-treat (ITT) effects of the *capital*, *psychosocial*, and *full* treatment respectively. These coefficients measure the average effect of being assigned to each treatment group compared to the control group. Given the randomized design, these estimates can be interpreted as causal effects as long as the randomization was properly implemented and there are no systematic differences in attrition across treatment arms. To account for the clustered nature of our data and potential correlation of outcomes within clusters, we compute standard errors clustered at the cluster level, which is the unit of randomization. 

**Additionally, we will present results both with and without baseline covariates and variables that are significantly different between treatment and control at baseline at the 10 percent level or lower to check the robustness of our findings and potentially improve precision.** (upcoming)



**Tekavoul Program** 

To estimate the impact of the national cash transfer program (Tekavoul) on IPV risk, the previous equation (1) is modified to the following equation:

$$
Y_{ic} = \theta_0 + \theta_1 CashAssignment_{c} + \theta_2 SP_{c} + \delta_{i} + \epsilon_{i} (2)
$$

Where \( \text{CashAssignment}_{c} \) is an indicator for the assignment to the Tekavoul cash transfer beneficiary of cluster \( c \). The coefficient \( \theta_1 \) represents the intent-to-treat (ITT) effect of the *cash assignment*.


# Results


```{r}

#####################################################################################
######################### Regression on the nbr of event ############################
#####################################################################################

# Define the list of outcomes variables

control_ipv_vars <- c("control_ipv_sev_12m","control_ipv_sev_index")
emotional_ipv_vars <- c("emo_ipv_sev_12m", "emo_ipv_sev_index") #"emo_ipv_inten_index","emo_sev_12m",
physical_ipv_vars <- c("phy_ipv_sev_12m","phy_ipv_sev_index")
sexual_ipv_vars <- c("sex_ipv_sev_12m", "sex_ipv_sev_index") #"sex_ipv_inten_index","sex_sev_12m",
sexual_physical_ipv_vars  <- c("sex_phy_ipv_sev_12m","sex_phy_ipv_sev_index")
economic_ipv_vars <- c("eco_ipv_sev_12m", "eco_ipv_sev_index") #"eco_ipv_inten_index","eco_sev_12m",
all_ipv_vars <- c("all_ipv_sev_12m","all_ipv_sev_index") #,"all2_ipv_12m"

# All outcomes variables
listOutcomes=c(control_ipv_vars, emotional_ipv_vars, physical_ipv_vars, sexual_ipv_vars, sexual_physical_ipv_vars, economic_ipv_vars, all_ipv_vars)


# Define the two treatment variables ("treatment_csh_trnsfr",)
treatment_vars=c("treatment_csh_trnsfr","treatment_pi","treatment_pi_pool")

# Label for the treatment variables
labels_vars = c("Cash transfert","Capital","Psychosocial","Full")

# Define controls variables for the regression 
control_vars = c(
                "pben_handicap_bl", 
                #"hhh_edu_bl", 
                #"pben_edu_bl", 
                "hhh_prim_bl",
                "pben_prim_bl", 
                #"age_at_mrrg", 
                "het_nbr_elder",
                #"age_gap",
                "hh_has_kid", 
                "het_wtht_adult_mal", 
                #"pben_lit_bl", 
                "hhh_fem_bl",
                #"mem_n_bl",
                "same_cb",
                #"hhh_poly",
                #"pben_poly",
                #"hhh_age",
                "pben_age_bl",
                "age_gap",
                "hhh_edu_bl",
                "pben_edu_bl",
                "hhh_lit_bl",
                "pben_lit_bl"
            # 
            # "ctrl_hh_index_tr_bl",
            # "consum",
            # "ctrl_earn_index_tr_bl",
            # "tot_hh_rev",
            # "hhh_age_bl",
            # "soc_cohsn_index_tr_bl",
            # "intrahh_vars_index_tr_bl",
            # "soc_stand_index_bl",
            # ##"rev_sum_bohh",
            # #"pben_age_bl",
            # # "age_gap",
            # # "nbr_hh_number",
            # "age_at_mrrg",
            # "region",
            #  "gse_index_tr_bl",
            #  "shr_adult",
            # "tot_ben_rev12_98_ppp_bl", 
            # "bus_assval_98_ppp_bl", 
            # "nbr_kid", 
            # "shr_adult_fem",
            # "tot_ben_pro12_98_ppp_bl", 
            # "nbr_adult_tot", 
            # #"hhh_edu_bl", 
            # #"shr_adult_mal", 
            # "nbr_adult",
            # "los1_bl", 
            # "shr_adult_fem_mal", 
            # "los2_bl", 
            # "dec_pow_bus_d_bl", 
            # "nbr_adult_fem_tot"
            )

# Define controls variables for the regression 
# control_vars = c(
#                 "pben_handicap_bl","hhh_fem_bl", "pben_fem_bl","age_gap",            "age_at_mrrg","het_shr_adult_mal",  "nbr_elder","shr_elder","nbr_kid"
#                 # "hhh_prim_bl",
#                 # "pben_prim_bl", 
#                 # "het_nbr_elder",
#                 # "hh_has_kid", 
#                 # "het_wtht_adult_mal", 
#                 # "hhh_fem_bl",
#                 # "same_cb",
#                 # "pben_age_bl",
#                 # "age_gap",
#                 # "hhh_edu_bl",
#                 # "pben_edu_bl",
#                 # "hhh_lit_bl",
#                 # "pben_lit_bl"
#             )


  # PRIORITY 1: Imbalanced variables that MUST be controlled
  # These showed statistical differences at baseline
  control_vars = c(
    # Demographics with imbalance
    #"age_gap",              # Significant in (2)-(3), Joint F-test
    
    
    # Elder/children with imbalance
    "nbr_elder",            # Significant in (1)-(2), (2)-(3), JoiÒnt F-test
    "het_nbr_elder",        # Significant in (1)-(2), (2)-(3), Joint F-test
    "shr_elder",            # Significant in (1)-(2), (2)-(3), Joint F-test
    
    # Education with imbalance
    "hhh_prim_bl",          # Significant in (1)-(4), (3)-(4), Joint F-test
    "pben_lit_bl",          # Significant in (1)-(2), (1)-(4), (2)-(3), (3)-(4), Joint F-test
    
    
    # Economic with imbalance
   "tot_emp_2rev12_ben_98_ppp_bl", # Significant in (1)-(2), (1)-(4), (2)-(4), Joint F-test
    
    # Business with imbalance
    "bus2_within_12_dum_ben_bl" # Significant in (1)-(3), (1)-(4), (2)-(4), Joint F-test, Pooled
  )
  
  # control_vars = c(
  #               "pben_handicap_bl",
  #               "hhh_prim_bl",
  #               "pben_prim_bl",
  #               "het_nbr_elder",
  #               "hh_has_kid",
  #               "het_wtht_adult_mal",
  #               "hhh_fem_bl",
  #               "same_cb",
  #               "pben_age_bl",
  #               "age_gap",
  #               "hhh_edu_bl",
  #               "pben_edu_bl",
  #               "hhh_lit_bl",
  #               "pben_lit_bl"
  #           )
  # 
# Define strata variables: strata
strata_vars <- c("strata") 

# Define cluster variables 
cluster_vars <- c("cluster")

followup_ipv_MRT_hh <- followup_ipv_MRT_hh %>% 
  mutate(strata = as.factor(strata),
         het_region = as.factor(het_region))

followup_ipv_MRT_hh <- followup_ipv_MRT_hh %>% 
  mutate(commune = as.factor(commune))


followup_ipv_MRT_hh_control_pi <- followup_ipv_MRT_hh %>% filter(treatment_pi=="Control") %>%
      filter(reg_hh_pi_mrt==1)

followup_ipv_MRT_hh_control_csh_trnsfr <- followup_ipv_MRT_hh %>% filter(treatment_csh_trnsfr=="Control") %>% 
      filter(reg_hh_csh_mrt==1)
# Title for each index
control_ipv_title = "**Table : effect of the program on controlling Behavior**"
emotional_ipv_title = "**Table : effect of the program on emotional violence**"
physical_ipv_title = "**Table : effect of the program on physical violence**"
sexual_ipv_title = "**Table : effect of the program on sexual violence**"
economic_ipv_title = "**Table : effect of the program on economic violence**"
other_ipv_title = "**Table : effect of the program on other ipv index**"
```

## Controlling Behavior

```{r}
# Controlling Behavior
tbl_control <- getTable_IPV(
  ipv_vars = control_ipv_vars,
  treatment_vars = treatment_vars,
  control_vars = control_vars,
  strata_vars = strata_vars,
  cluster_vars = cluster_vars,
  followup_ipv_MRT_hh = followup_ipv_MRT_hh,
  followup_ipv_MRT_hh_control_pi = followup_ipv_MRT_hh_control_pi,
  followup_ipv_MRT_hh_control_csh_trnsfr = followup_ipv_MRT_hh_control_csh_trnsfr,
  col_group_labels = c("Binary for control IPV in the last 12 months", "Control IPV sev. index"),
  table_title = "Controlling Behavior IPV Results"
)
tbl_control
```

## Emotional Violence

```{r}
# Emotional Violence
tbl_emotional <- getTable_IPV(
  ipv_vars = emotional_ipv_vars,
  treatment_vars = treatment_vars,
  control_vars = control_vars,
  strata_vars = strata_vars,
  cluster_vars = cluster_vars,
  followup_ipv_MRT_hh = followup_ipv_MRT_hh,
  followup_ipv_MRT_hh_control_pi = followup_ipv_MRT_hh_control_pi,
  followup_ipv_MRT_hh_control_csh_trnsfr = followup_ipv_MRT_hh_control_csh_trnsfr,
  col_group_labels = c("Binary for emo. IPV in the last 12 months", "Emo. IPV sev. index"),
  table_title = "Emotional Violence IPV Results"
)
tbl_emotional
```


## Physical Violence

```{r}
# Physical Violence
tbl_physical <- getTable_IPV(
  ipv_vars = physical_ipv_vars,
  treatment_vars = treatment_vars,
  control_vars = control_vars,
  strata_vars = strata_vars,
  cluster_vars = cluster_vars,
  followup_ipv_MRT_hh = followup_ipv_MRT_hh,
  followup_ipv_MRT_hh_control_pi = followup_ipv_MRT_hh_control_pi,
  followup_ipv_MRT_hh_control_csh_trnsfr = followup_ipv_MRT_hh_control_csh_trnsfr,
  col_group_labels = c("Binary for phy. IPV in the last 12 months", "Phy. IPV sev. index"),
  table_title = "Physical Violence IPV Results"
)
tbl_physical
```

## Sexual Violence

```{r}
# Sexual Violence
tbl_sexual <- getTable_IPV(
  ipv_vars = sexual_ipv_vars,
  treatment_vars = treatment_vars,
  control_vars = control_vars,
  strata_vars = strata_vars,
  cluster_vars = cluster_vars,
  followup_ipv_MRT_hh = followup_ipv_MRT_hh,
  followup_ipv_MRT_hh_control_pi = followup_ipv_MRT_hh_control_pi,
  followup_ipv_MRT_hh_control_csh_trnsfr = followup_ipv_MRT_hh_control_csh_trnsfr,
  col_group_labels = c("Binary for sex. IPV in the last 12 months", "Sex. IPV sev. index"),
  table_title = "Sexual Violence IPV Results"
)

tbl_sexual
```

## Sexual or Physical Violence
```{r}
# Sexual or Physical Violence
tbl_sexual_physical <- getTable_IPV(
  ipv_vars = sexual_physical_ipv_vars,
  treatment_vars = treatment_vars,
  control_vars = control_vars,
  strata_vars = strata_vars,
  cluster_vars = cluster_vars,
  followup_ipv_MRT_hh = followup_ipv_MRT_hh,
  followup_ipv_MRT_hh_control_pi = followup_ipv_MRT_hh_control_pi,
  followup_ipv_MRT_hh_control_csh_trnsfr = followup_ipv_MRT_hh_control_csh_trnsfr,
  col_group_labels = c("Binary for phy. or sex. IPV in the last 12 months", "Phy. or sex. IPV sev. index"),
  table_title = "Sexual or Physical Violence IPV Results"
)
tbl_sexual_physical
```

## Economic Violence

```{r}
# Economic Violence
tbl_economic <- getTable_IPV(
  ipv_vars = economic_ipv_vars,
  treatment_vars = treatment_vars,
  control_vars = control_vars,
  strata_vars = strata_vars,
  cluster_vars = cluster_vars,
  followup_ipv_MRT_hh = followup_ipv_MRT_hh,
  followup_ipv_MRT_hh_control_pi = followup_ipv_MRT_hh_control_pi,
  followup_ipv_MRT_hh_control_csh_trnsfr = followup_ipv_MRT_hh_control_csh_trnsfr,
  col_group_labels = c("Binary for eco. IPV in the last 12 months", "Eco. IPV sev. index"),
  table_title = "Economic Violence IPV Results"
)
tbl_economic
```


## All types of violence

```{r}
# All types of violence
tbl_all <- getTable_IPV(
  ipv_vars = all_ipv_vars,
  treatment_vars = treatment_vars,
  control_vars = control_vars,
  strata_vars = strata_vars,
  cluster_vars = cluster_vars,
  followup_ipv_MRT_hh = followup_ipv_MRT_hh,
  followup_ipv_MRT_hh_control_pi = followup_ipv_MRT_hh_control_pi,
  followup_ipv_MRT_hh_control_csh_trnsfr = followup_ipv_MRT_hh_control_csh_trnsfr,
  col_group_labels = c("Binary for at least one type of IPV (exclu. eco.) in the last 12 months", "All IPV (exclu. eco.) sev. index"),
  table_title = "All Types of Violence IPV Results"
)

tbl_all
```

# Heterogenous effect

```{r}

####################### Second estimate #########################################
# lst_outcomes=c("olderchild_s","earlychild_s", "adult_fem_s")

# Define a list of heterogeneity variables to examine for differential treatment effects
lst_het_var <- c(
  "het_hhh_fem",          # Household head is female
  "het_hhh_edu",          # Household head nbr. year of education
  "het_pben_edu",         # Beneficiary nbr. year of education
  "het_hhh_lit",          # Partner literacy
  "het_pben_lit",          # Beneficiary literacy
  "het_save_share",         # Share of saving own by partner
  "het_ctrl_earn_index",  # Beneficiary control over earnings index
  "het_ctrl_hh_index",    # Control over household decisions index
  "het_intrahh_index",    # Beneficiary intra-household dynamics index
  "het_age_gap",           # Age gap between partners
  "het_consum",   # Consumption
  "het_age_at_mrrg_above18",   # Married after 18
  "het_age_at_mrrg",   # Married after median age of marriage
  "het_region", # Region (1= Selibabi 0=barkeol)
  "het_consum_eq", # Consumpt. per adult eq. at bl.
  "het_lauch_bus", # Ben lauch business
  "het_create_bus", # Ben create business
  "het_has_bus", # Ben has business at baseline
  "het_bp_index" # Ben decision making index
)

# Create a data frame of results examining heterogeneous treatment effects
# across different economic IPV outcomes, treatment variables, and heterogeneity dimensions
mainResults_het <- map_dfr(listOutcomes, function(depvar) {
 
   # For each heterogeneity variable...
  tempResults1 <- map_dfr(lst_het_var, function(het_var) { 
  
    # For each treatment variable...
    tempResults2 <- map_dfr(treatment_vars, function(treat_var) {

      bind_rows(
        # Get estimates for heterogeneous treatment effects using the specified model
        getEstimateGlobal_het(depvar, treat_var, het_var, control_vars, strata_vars, cluster_vars, followup_ipv_MRT_hh) %>%
          # Add columns identifying which variables were used in this iteration
          mutate(depvar = depvar, outcome = depvar, treat_var = treat_var, het_var = het_var)
        )
    })
  })
})

#  Mutate and recode variables for better readability
mainResults_het <- mainResults_het %>%
    mutate(
        # Recode 'name' variable
      name = dplyr::recode(name,
        cash = "(a) Tekavoul program",
        pi = "(b) Economic inclusion program"
      ),
      het_var = dplyr::recode(het_var,
                      het_hhh_edu="Prtnr nbr. yrs of educ.",
                      het_pben_edu="Benef. nbr. yrs of educ.",
                      het_hhh_lit = "Prtnr literacy",
                      het_pben_lit = "Benef. literacy",
                      het_save_share = "Shr of resources own by prtnr",
                      het_ctrl_earn_index = "Cntrl earn. index",
                      het_ctrl_hh_index = "Cntrl hh. resources index",
                      het_intrahh_index = "Intra-hh. dynamics index",
                      het_rev_sum_bohh = "Benef. share of total hh. rev.",
                      het_age_gap = "Age gap (prtnr - benef.)",
                      het_region = "Household in Sélibaby",
                      het_tot_hh_rev = "Tot. hh. revenue at bl.",
                      het_consum = "Consumption eq ppp at bl.",
                      het_age_at_mrrg_above18 = "Benef. married after 18",
                      het_age_at_mrrg = "Benef. age at marriage",
                      het_consum_eq = "Consumpt. per adult eq. at bl.",
  het_lauch_bus = "Benef. lauch. a bus.",
  het_create_bus = "Benef. creat. a bus.",
  het_has_bus = "Benef. has a bus. at bl.",
  het_bp_index = "Benef. decis. making index",
  het_bp_index_2 = "Benef. decis. making index 2"
      ),
        # Recode 'estimate' variable
      estimate = dplyr::recode(
        estimate,
        No = "low",
        Yes = "high"
      ),
        depvar = dplyr::recode(depvar,
              control_ipv_sev_12m = "Controlling Behavior (Binary)",
              control_ipv_sev_index = "Controlling Behavior severity index (continuous)",
              emo_ipv_sev_12m = "Emotional IPV (Binary)",
              emo_ipv_sev_index = "Emotional IPV severity index (continuous)",
              phy_ipv_sev_12m = "Physical IPV (Binary)", 
              phy_ipv_sev_index = "Physical IPV severity index (continuous)",
              sex_ipv_sev_12m = "Sexual IPV (Binary)", 
              sex_ipv_sev_index = "Sexual IPV severity index (continuous)",
              sex_phy_ipv_sev_12m = "Physical or sexual IPV (Binary)", 
              sex_phy_ipv_sev_index = "Physical or sexual IPV severity index (continuous)",
  
              eco_ipv_sev_12m = "Economic IPV (Binary)", 
              eco_ipv_sev_index = "Economic IPV severity index (continuous)",
              all_ipv_sev_12m = "Emotional, physical or sexual IPV (Binary)", 
              all_ipv_sev_index = "Emotional, physical or sexual IPV index (continuous)"
      )
      )


    # Compute proportions by category
mainResults_het <- mainResults_het %>%
  group_by(depvar, name, het_var, typeTreat) %>%
  mutate(N_treat = sum(Ntype_treat)) %>%
  ungroup() %>%
  mutate(prop = round(Ntype_treat * 100 / N_treat, 2))

# Generate labels for the plot
  mainResults_het <- mainResults_het %>%
    group_by(depvar, name, het_var, typeTreat) %>%
    mutate(
      lab = sprintf(
        "%s \n N high treat (pct): %s (%s)\n N low treat (pct): %s (%s)",
        first(typeTreat),
        scales::comma(last(Ntype_treat)),
        scales::comma(last(prop)),
        scales::comma(first(Ntype_treat)),
        scales::comma(first(prop))
      )
    ) %>%
    ungroup()


  # Generate unique label for every one
  mainResults_het <- mainResults_het %>%
    group_by(name, het_var, typeTreat) %>%
    mutate(
      lab = first(lab)
      )%>%
    ungroup()
  
median_val <- map_dfr(gsub("het_", "", lst_het_var, fixed = TRUE), ~{
    followup_ipv_MRT_hh %>% 
        summarize(
            het_var = .x,  # Add het variable name for clarity in output
            median_value = round(median(!!sym(.x), na.rm = TRUE), 2)
        )}) %>%
  mutate(      
  het_var = dplyr::recode(het_var,
                      hhh_edu="Prtnr nbr. yrs of educ.",
                      pben_edu="Benef. nbr. yrs of educ.",
                      hhh_lit = "Prtnr literacy",
                      pben_lit = "Benef. literacy",
                      save_share = "Shr of resources own by prtnr",
                      ctrl_earn_index = "Cntrl earn. index",
                      ctrl_hh_index = "Cntrl hh. resources index",
                      intrahh_index = "Intra-hh. dynamics index",
                      rev_sum_bohh = "Benef. share of total hh. rev.",
                      age_gap = "Age gap (prtnr - benef.)",
                      region = "Household in Sélibaby",
                      tot_hh_rev = "Tot. hh. revenue at bl.",
                      consum = "Consumption eq ppp at bl.",
                      age_at_mrrg_above18 = "Benef. married after 18",
                      age_at_mrrg = "Benef. age at marriage",
                      consum_eq = "Consumpt. per adult eq. at bl.",
  lauch_bus = "Benef. lauch. a bus.",
  create_bus = "Benef. creat. a bus.",
  has_bus = "Benef. has a bus. at bl.",
  bp_index = "Benef. decis. making index",
  bp_index_2 = "Benef. decis. making index 2"
      ))
```

## Controlling Behavior 

```{r}
#curr_outcome = control_ipv_vars
 curr_outcome = "control_ipv_sev_12m"
```

### Partner literacy
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Prtnr literacy",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)

```

### Beneficiary literacy

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. literacy",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)

```

### Partner nbr. of years of education

```{r}
plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Prtnr nbr. yrs of educ.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```

### Beneficiary nbr. of years of education

```{r}
plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. nbr. yrs of educ.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)

```

### Beneficiary control over earnings

```{r}
plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Cntrl earn. index",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)

```

### Beneficiary control over hh. resources

```{r}
plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Cntrl hh. resources index",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```

### Beneficiary intra-household dynamics 

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Intra-hh. dynamics index",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```


### Spousal age gap

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Age gap (prtnr - benef.)",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```


### Beneficiary age at marriage 

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. age at marriage",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```


### Beneficiary married after 18 

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. married after 18",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```


### Consumption at baseline

```{r}
plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Consumption eq ppp at bl.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```

### Region
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Household in Sélibaby",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```

### Consumpt. per adult eq. at bl.

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Consumpt. per adult eq. at bl.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```

### Beneficiary lauched a business
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. lauch. a bus.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```

### Beneficiary created a business
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. creat. a bus.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```

### Beneficiary has a business 
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. has a bus. at bl.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```

### Beneficiary decision making index
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. decis. making index",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```


### Beneficiary decision making index 2
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. decis. making index 2",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```

## Emotional Violence

```{r}
curr_outcome = emotional_ipv_vars
```

### Partner literacy
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Prtnr literacy",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)

```

### Beneficiary literacy

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. literacy",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)

```

### Partner nbr. of years of education

```{r}
plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Prtnr nbr. yrs of educ.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```

### Beneficiary nbr. of years of education

```{r}
plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. nbr. yrs of educ.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)

```

### Beneficiary control over earnings

```{r}
plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Cntrl earn. index",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)

```

### Beneficiary control over hh. resources

```{r}
plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Cntrl hh. resources index",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```

### Beneficiary intra-household dynamics 

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Intra-hh. dynamics index",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```


### Spousal age gap

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Age gap (prtnr - benef.)",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```


### Beneficiary age at marriage 

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. age at marriage",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```


### Beneficiary married after 18 

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. married after 18",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```


### Consumption at baseline

```{r}
plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Consumption eq ppp at bl.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```

### Region
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Household in Sélibaby",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```

### Consumpt. per adult eq. at bl.

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Consumpt. per adult eq. at bl.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```

### Beneficiary lauched a business
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. lauch. a bus.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```

### Beneficiary created a business
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. creat. a bus.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```

### Beneficiary has a business 
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. has a bus. at bl.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```

### Beneficiary decision making index
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. decis. making index",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```


### Beneficiary decision making index 2
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. decis. making index 2",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```

## Physical violence

```{r}
curr_outcome = physical_ipv_vars
```

### Partner literacy
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Prtnr literacy",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)

```

### Beneficiary literacy

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. literacy",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)

```

### Partner nbr. of years of education

```{r}
plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Prtnr nbr. yrs of educ.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```

### Beneficiary nbr. of years of education

```{r}
plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. nbr. yrs of educ.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)

```

### Beneficiary control over earnings

```{r}
plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Cntrl earn. index",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)

```

### Beneficiary control over hh. resources

```{r}
plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Cntrl hh. resources index",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```

### Beneficiary intra-household dynamics 

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Intra-hh. dynamics index",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```


### Spousal age gap

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Age gap (prtnr - benef.)",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```


### Beneficiary age at marriage 

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. age at marriage",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```


### Beneficiary married after 18 

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. married after 18",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```


### Consumption at baseline

```{r}
plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Consumption eq ppp at bl.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```

### Region
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Household in Sélibaby",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```


### Consumpt. per adult eq. at bl.

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Consumpt. per adult eq. at bl.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```

### Beneficiary lauched a business
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. lauch. a bus.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```

### Beneficiary created a business
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. creat. a bus.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```

### Beneficiary has a business 
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. has a bus. at bl.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```

### Beneficiary decision making index
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. decis. making index",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```


### Beneficiary decision making index 2
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. decis. making index 2",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```

## Sexual Violence 

```{r}
#curr_outcome = sexual_ipv_vars
curr_outcome = "sex_ipv_sev_12m"
```

### Partner literacy
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Prtnr literacy",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)

```

### Beneficiary literacy

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. literacy",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)

```

### Partner nbr. of years of education

```{r}
plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Prtnr nbr. yrs of educ.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```

### Beneficiary nbr. of years of education

```{r}
plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. nbr. yrs of educ.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)

```

### Beneficiary control over earnings

```{r}
plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Cntrl earn. index",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)

```

### Beneficiary control over hh. resources

```{r}
plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Cntrl hh. resources index",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```

### Beneficiary intra-household dynamics 

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Intra-hh. dynamics index",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```


### Spousal age gap

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Age gap (prtnr - benef.)",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```


### Beneficiary age at marriage 

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. age at marriage",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```


### Beneficiary married after 18 

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. married after 18",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```


### Consumption at baseline

```{r}
plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Consumption eq ppp at bl.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```

### Region
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Household in Sélibaby",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```

### Consumpt. per adult eq. at bl.

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Consumpt. per adult eq. at bl.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```

### Beneficiary lauched a business
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. lauch. a bus.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```

### Beneficiary created a business
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. creat. a bus.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```

### Beneficiary has a business 
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. has a bus. at bl.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```

### Beneficiary decision making index
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. decis. making index",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```


### Beneficiary decision making index 2
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. decis. making index 2",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```

## Physical and sexual violence 

```{r}
curr_outcome = sexual_physical_ipv_vars
```

### Partner literacy
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Prtnr literacy",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)

```

### Beneficiary literacy

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. literacy",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)

```

### Partner nbr. of years of education

```{r}
plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Prtnr nbr. yrs of educ.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```

### Beneficiary nbr. of years of education

```{r}
plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. nbr. yrs of educ.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)

```

### Beneficiary control over earnings

```{r}
plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Cntrl earn. index",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)

```

### Beneficiary control over hh. resources

```{r}
plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Cntrl hh. resources index",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```

### Beneficiary intra-household dynamics 

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Intra-hh. dynamics index",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```


### Spousal age gap

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Age gap (prtnr - benef.)",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```


### Beneficiary age at marriage 

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. age at marriage",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```


### Beneficiary married after 18 

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. married after 18",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```


### Consumption at baseline

```{r}
plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Consumption eq ppp at bl.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```

### Region
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Household in Sélibaby",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```


### Consumpt. per adult eq. at bl.

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Consumpt. per adult eq. at bl.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```

### Beneficiary lauched a business
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. lauch. a bus.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```

### Beneficiary created a business
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. creat. a bus.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```

### Beneficiary has a business 
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. has a bus. at bl.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```

### Beneficiary decision making index
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. decis. making index",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```


### Beneficiary decision making index 2
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. decis. making index 2",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```

## Economic Violence 

```{r}
curr_outcome = economic_ipv_vars
```

### Partner literacy
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Prtnr literacy",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)

```

### Beneficiary literacy

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. literacy",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)

```

### Partner nbr. of years of education

```{r}
plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Prtnr nbr. yrs of educ.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```

### Beneficiary nbr. of years of education

```{r}
plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. nbr. yrs of educ.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)

```

### Beneficiary control over earnings

```{r}
plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Cntrl earn. index",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)

```

### Beneficiary control over hh. resources

```{r}
plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Cntrl hh. resources index",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```

### Beneficiary intra-household dynamics 

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Intra-hh. dynamics index",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```


### Spousal age gap

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Age gap (prtnr - benef.)",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```


### Beneficiary age at marriage 

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. age at marriage",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```


### Beneficiary married after 18 

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. married after 18",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```


### Consumption at baseline

```{r}
plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Consumption eq ppp at bl.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```

### Region
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Household in Sélibaby",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```


### Consumpt. per adult eq. at bl.

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Consumpt. per adult eq. at bl.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```

### Beneficiary lauched a business
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. lauch. a bus.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```

### Beneficiary created a business
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. creat. a bus.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```

### Beneficiary has a business 
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. has a bus. at bl.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```

### Beneficiary decision making index
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. decis. making index",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```


### Beneficiary decision making index 2
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. decis. making index 2",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```

## All types of violence

```{r}
curr_outcome = all_ipv_vars
curr_outcome = "all_ipv_sev_12m"
```

### Partner literacy
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Prtnr literacy",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)

```

### Beneficiary literacy

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. literacy",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)

```

### Partner nbr. of years of education

```{r}
plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Prtnr nbr. yrs of educ.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```

### Beneficiary nbr. of years of education

```{r}
plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. nbr. yrs of educ.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)

```

### Beneficiary control over earnings

```{r}
plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Cntrl earn. index",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)

```

### Beneficiary control over hh. resources

```{r}
plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Cntrl hh. resources index",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```

### Beneficiary intra-household dynamics 

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Intra-hh. dynamics index",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```


### Spousal age gap

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Age gap (prtnr - benef.)",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```


### Beneficiary age at marriage 

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. age at marriage",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```


### Beneficiary married after 18 

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. married after 18",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```


### Consumption at baseline

```{r}
plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Consumption eq ppp at bl.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```

### Region
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Household in Sélibaby",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```


### Consumpt. per adult eq. at bl.

```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Consumpt. per adult eq. at bl.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```

### Beneficiary lauched a business
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. lauch. a bus.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```

### Beneficiary created a business
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. creat. a bus.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```

### Beneficiary has a business 
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. has a bus. at bl.",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```

### Beneficiary decision making index
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. decis. making index",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = FALSE
)
```


### Beneficiary decision making index 2
```{r}

plot_het_ipv(
  depvar_group = curr_outcome,
  curr_het_var = "Benef. decis. making index 2",
  mainResults_het = mainResults_het,
  median_val      = median_val,
  binary_het      = TRUE
)
```

```{r}
# remove data to free space
rm(list = ls())
```
