---
title: "Cash Plus, Safety Plus? Intimate Partner Violence and Productive Inclusion in Mauritania"
subtitle: "Mechanism"
author: "IBRAHIM KASSOUM Habibou"
date: '`r format (Sys.Date(), "%d %B %Y")`'
output: 
  officedown::rdocx_document:
    mapstyles:
      Normal: ['First Paragraph']
---


```{r setup, include=FALSE}
# Set random seed for reproducibility
set.seed(7654)

# Set number of decimal places to display
options(digits = 3)

# Configure knitr chunk options:
knitr::opts_chunk$set(
 echo = FALSE,          # Don't show R code in output
 message = FALSE,       # Don't show messages
 warning = FALSE,       # Don't show warnings
 cache = FALSE,         # Don't cache results
 fig.align = 'center',  # Center figures
 fig.width = 6.3,         # Figure width in inches
 fig.height= 7,          # Figure height in inches
 fig.asp = 0.8,       # Figure aspect ratio (golden ratio)
 fig.show = "hold"      # Hold multiple plots until end of chunk
)

# Set dplyr print options to show 6 rows max
options(dplyr.print_min = 6, dplyr.print_max = 6)

# Set max vector size
mem.maxVSize(vsize = Inf)
# Sometimes temporary files accumulate and cause issues. You can clear them manually or use:
#unlink(tempdir(), recursive = TRUE)
```


```{r, include=FALSE, results='hide', echo=FALSE}

######################## Importing library and external files ##################
### List of required packages
required_packages <- c("tidyverse", "dplyr","officedown", "officer", "gtsummary",
                       "stargazer", "lfe","labelled","car","purrr", "flextable","remotes")

### Check if packages are installed
missing_packages <- setdiff(required_packages, installed.packages()[,"Package"])

### Install missing packages
if (length(missing_packages) > 0) {
  install.packages(missing_packages)
}

### Load all packages
lapply(required_packages, library, character.only = TRUE)

# Remove all objects
rm(list = ls())

# Source functions from external file
source("functions.R")

#  Importing module to concatenate several model
#remotes::install_github("ChandlerLutz/starpolishr")
```



```{r echo=F}

set_gtsummary_theme(theme_gtsummary_compact())

######### Create default BioAVR table from dataframe
#
# Dependencies : dplyr, flextable, officer
# source link : https://www.r-bloggers.com/2021/11/publication-ready-tables-with-flextable-and-own-theme-in-r/
customtab_defaults <- function(){
set_flextable_defaults(font.family = "Times New Roman",
font.size = 10,
border.color = "black")
}
FitFlextableToPage <- function(ft, pgwidth = 8){

  ft_out <- ft %>% autofit()

  ft_out <- width(ft_out, width = dim(ft_out)$widths*pgwidth /(flextable_dim(ft_out)$widths))
  return(ft_out)
}
custom_tab <- function(df, header, footer){
flextable(df) %>%
add_header_lines(header) %>%
add_footer_lines(footer) %>%
bold(i = 1, part = "header") %>%
hline_top(part = "header",
border = fp_border(color = "white",
width = 3,
style = "solid")) %>%
hline(i = 1,
part = "header",
border = fp_border(color = "black",
width = 0.25,
style = "solid")) %>%
hline_top(part = "body",
border = fp_border(color = "black",
width = 0.25,
style = "solid")) %>%
hline_bottom(part = "body",
border = fp_border(color = "black",
width = 0.25,
style = "solid")) %>%
hline_bottom(part = "footer",
border = fp_border(color = "black",
width = 0.25,
style = "solid")) %>%
border_inner_h(part = "body",
border = fp_border(color = "black",
width = 0.25,
style = "dotted")) %>%
autofit(part = "body") %>%
bg(part = "body", bg = "white") %>%
align(part = "all", align = "center") %>%
align(j = 1, part = "all", align = "left")
}
```


```{r}

######################## Loading the datasets ##################################
# Read the file containing the global dataframe into followup_MRT_hh

followup_MRT_hh <- readRDS(paste0(getwd(),"/output/data/followup_MRT_hh_and_ipv_MRT_hh.rds"))

# Creating some variables at partner level
followup_MRT_hh <- followup_MRT_hh %>% 
  mutate(rev_sum_prt_wemp_98 = rev_sum_hh_wemp_98 - rev_sum_ben_wemp_98,  
         tot_prt_rev12_98_ppp = tot_hh_rev12_98_ppp - tot_ben_rev12_98_ppp,   
         tot_emp_2rev12_prt_98_ppp = tot_emp_2rev12_hh_98_ppp - tot_emp_2rev12_ben_98_ppp,  
         tot_ani_prt_contr_98_ppp = tot_ani_hh_contr_98_ppp - tot_ani_ben_contr_98_ppp)



# Convert treatment variables from numeric to factor variables for both datasets
# This is useful for regression analysis and plotting as factors are treated as categorical variables
 # Convert PM treatment to factor
followup_MRT_hh$treatment_pi <- haven::as_factor(followup_MRT_hh$treatment_pi)

# Convert cash transfer treatment to factor
followup_MRT_hh$treatment_csh_trnsfr <- haven::as_factor(followup_MRT_hh$treatment_csh_trnsfr)
followup_MRT_hh_control <- followup_MRT_hh %>% filter(treatment_pi == "Control" | treatment_csh_trnsfr == "Control") 

# Define controls variables for the regression 
control_vars = c("hhh_fem_bl", 
            "mem_n_bl",
            "same_cb",
            "pben_handicap",
            "hhh_poly",
            "pben_poly",
            "hhh_age",
            "pben_age",
            "age_gap",
            "hhh_edu",
            "pben_edu",
            "hhh_lit",
            "pben_lit")

# List of outcomes definition mechanism
#----------------------------------------
# Revenue and Consumption Outcome Variables
#----------------------------------------
revenue_consum_vars_hh <- c(
  "consum_2_day_eq_ppp",        # Consumption per capita (PPP-adjusted)
  "food_2_day_eq_ppp", 	# "Food\n consumption\n (daily, USD/adult eq.)"
  "nonfood_day_eq_ppp",	 # Non food consumption
  "eatout_day_eq_ppp",	#"Eating out\n expenditure\n (daily, USD/adult eq.)"
	"edu_day_eq_ppp", # Education expenditures
  "health_day_eq_ppp", # Health expenditures
  "cel_day_eq_ppp", # # Celebration expenditures
  "ton_or_avec_hh", # "Takes part in\n tontine/AVEC\n \{0,1\}"
  "tot_cred_out_ppp", #  "Total\n debt\n (yearly, USD)"	
  "tot_cred_amt_ppp", #  "Total\n borrowed\n (yearly, USD)"
  "gross_trans_ppp", #"Household\n Gross transfers\n (yearly, USD)"
  "saving_ppp", # Saving tot
  "FIES_rvrs_raw",            # Food Insecurity Experience Scale (reversed)
  "FCS",                      # Food Consumption Score

  # Revenue-related variables
  "rev_sum_hh_wemp_98",       # Total household revenue from work (women employment sample, 98th
  "tot_hh_rev12_98_ppp",      # Total household revenue in past 12 months (98th pctl, PPP)
  "tot_emp_2rev12_hh_98_ppp", # Total employment-related revenue over 12 months (winsorized 98th pctl)
  "tot_ani_hh_contr_98_ppp",
  
  # Income diversification variables
  "all_income_cat",           # Number of income categories
  "all_income_div",           # Income diversification index
  "div_emp12_n"              # Number of employment sources over 12 months
)

revenue_consum_vars_ben <- c(
  # Revenue-related variables
  "rev_sum_hh_wemp_98",
  "rev_sum_ben_wemp_98",       # Total ben revenue from work (women employment sample, 98th percentile winsorized)
  "rev_sum_prt_wemp_98",
  "tot_hh_rev12_98_ppp", 
  "tot_ben_rev12_98_ppp",      # Total ben revenue in past 12 months (98th pctl, PPP)
  "tot_prt_rev12_98_ppp",
  "tot_emp_2rev12_hh_98_ppp",
  "tot_emp_2rev12_ben_98_ppp", # Total ben employment-related revenue over 12 months (winsorized 98th pctl)
  "tot_emp_2rev12_prt_98_ppp",
  "tot_ani_hh_contr_98_ppp",
  "tot_ani_ben_contr_98_ppp",
  "tot_ani_prt_contr_98_ppp"
)


#----------------------------------------
# Intra-household dynamics index
#----------------------------------------
intra_hh_vars <- c(
  "intrahh_vars_index",       # Composite index of intra-household dynamics
  "dom_relation_index",       # Index of domestic relationship/violence perception
  "gender_attitudes_index"    # Index measuring gender role attitudes
)

#----------------------------------------
# Time Use Variables (hours or dummies)
#----------------------------------------
time_use_int <- c(
  # Weekly time use by activity
  "time_wk_ben_nonag",        # Time in non-ag activities
  "time_wk_ben_water",        # Time fetching water
  "time_wk_ben_cook",         # Time cooking
  "time_wk_ben_ag",           # Time in agricultural activities
  "time_wk_ben_firewood",     # Time collecting firewood
  "time_wk_ben_clean",        # Time cleaning
  "time_wk_ben_study_coran",  # Time studying the Quran
  "time_wk_ben_laundry",      # Time doing laundry
  "time_wk_ben_liv",          # Time in livestock activities
  "time_wk_ben_study_trad",   # Time in traditional study
  "time_wk_ben_shop",         # Time shopping
  "time_wk_ben_child",           # Time with children
  "time_wk_ben_handicap",        # Time with disabled
  "time_wk_ben_family",          # Time with friends
  "time_wk_ben_radio",           # Time listening to radio
  "time_wk_ben_rest",            # Time resting
  "time_wk_ben_study_trad",   # Time studying traditional school
  "time_wk_ben_shop",            # Time spent shopping
  "time_wk_ben_pray"            # Time praying
)



time_use_ext <- c(

  # Dummy variables indicating whether these activities were done
  "time_ben_nonag_d", "time_ben_ag_d", "time_ben_study_coran_d", 
  "time_ben_study_trad_d", "time_ben_water_d","time_ben_firewood_d", 
  "time_ben_laundry_d", "time_ben_shop_d", "time_ben_cook_d", "time_ben_clean_d",
  "time_ben_liv_d", "time_ben_child_d", "time_ben_handicap_d", "time_ben_family_d",
  "time_ben_radio_d", "time_ben_rest_d", "time_ben_study_trad_d","time_ben_shop_d",
  "time_ben_pray_d"
)

#----------------------------------------
# Decision-Making and Control Over Income
#----------------------------------------
dec_making <- c(
  "ctrl_hh_index",            # Index of control over household decisions
  "ctrl_earn_index",          # Index of control over earnings
  "dec_pow_earn", "dec_could_earn",      # Power/capacity to earn
  "dec_pow_ag", "dec_pow_liv", "dec_pow_bus",  # Power in productive sectors
  "dec_pow_spend", "dec_could_spend", "dec_pow_large", "dec_could_large",
  "dec_pow_fert", "dec_could_fert", "dec_pow_care", "dec_could_care",
  "dec_pow_his_earn", "dec_pow_edu"
  
)


#----------------------------------------
# Intra-household Index Components
#----------------------------------------
intra_hh_index_components_vars <- c(
  "intrahh_vars_index",        # Overall intra-HH index
  "partner_vars_index",        # Partner dynamics index
  "hh_vars_index",             # General HH relationship index
  "rel_disagree",   # Relational and employment conflict indicators
  "rel_interest", "los3", "los1", "tens_house",  # Loss/tension/stress indicators
  "stair_satis_today"
)


#----------------------------------------
# Index Components: Social Norms
#----------------------------------------
social_norm_index_components_vars <- c(
  "soc_norms_index",           # Composite social norms index
  "dscrptv_norms_index",       # Descriptive norms
  "ten_support", "ten_loan", "ten_new", "ten_travel",  # Support/loan/social mobility
  "prscrptv_norms_index",      # Prescriptive norms
  "ten_mentravel_rvrs", "ten_menown_rvrs",             # Norms about men
  "ten_womentravel_rvrs", "ten_womenown_rvrs"          # Norms about women
)

#----------------------------------------
# Index Components: Gender Attitudes
#----------------------------------------
gender_attitudes_index_components_vars <- c(
  "gender_attitudes_index",    # Overall gender attitude index
  "dom_burn", "dom_kids",    # Household duties perceptions
  "ten_violen", "ten_men", "ten_boys"  # Violence/gender roles
)

#----------------------------------------
# Index Components: Perceptions of Violence
#----------------------------------------
violence_prcptn_index_components_vars <- c(
  "dom_relation_index", "ten_tension",   # Domestic tension/perceptions
  "vill_burn", "vill_kids"               # Village level violence indicators
)

#----------------------------------------
# Index Components: Control Over Earnings
#----------------------------------------
ctrl_over_earn_index_components_vars <- c(
  "ctrl_earn_index",          # Index of control over earnings
  "dec_pow_earn", "dec_could_earn",      # Power/capacity to earn
  "dec_pow_ag", "dec_pow_liv", "dec_pow_bus",  # Power in productive sectors
  "crop_ctrl_dum", "bus2_ben_dum", "ani_ben_dum", "ani_contr_ben_dum", "sleep_prod_dum"  # Decision control variables
)

#----------------------------------------
# Index Components: Control Over Household
#----------------------------------------
ctrl_hh_index_components_vars <- c(
  "ctrl_hh_index", "dec_pow_spend", "dec_could_spend", "dec_pow_large", "dec_could_large",
  "dec_pow_fert", "dec_could_fert", "dec_pow_care", "dec_could_care",
  "dec_pow_his_earn", "dec_pow_edu"
)

#----------------------------------------
# Mental Health Index Components
#----------------------------------------
mental_health_index_components_vars <- c(
  "ment_hlth_index",           # Mental health index
  "less_depressed", "less_disability",  # Depression and disability indicators
  "stair_satis_today", "stairs_peace",  # Life satisfaction and peace of mind
  "health_ment_z"              # Z-score of mental health
)



empowerment <- c(
  "dec_could_earn", 			# decision could earn
  "tot_emp_2rev12_ben_98_ppp", 		#"Wage\n earnings\n (yearly, USD)"
	"crop_ctrl_dum", 	#"Benef. controls\n crop\n revenue \{0,1\}"
  "na_bus2_op_wn_12_ben", # No. of\n beneficiary\n businesses
  "bus2_ben_dum",	 	#"Beneficiary\n has a\n business \{0,1\}"
  "tot_busmths_uniq_ben", #No. of months benef worked last year
  "div_n_na_12_ben", # Entrepreneurial\n business types\n (yearly)
  "bus2_within_12_dum_ben",	#Beneficiary\n launched a\n business \{0,1\}				
	"bus2_abandon_24_dum_ben", # Beneficiary\n abandoned a\n business \{0,1\}
  "tot_put_1_ppp", 		#"Personnal\n savings"
  "tot_ben_rev12_98_ppp", # Business\n revenues\n (yearly, USD)    	
	"tot_ben_pro12_98_ppp", # Business\n profits\n (yearly, USD)
  "bus_assval_ben_98_ppp", # Business\n asset\n value (USD)
  "bus2_invest_ppp", # Beneficiary\n investments\n (yearly, USD)
  'tot_ben_rev30_98_ppp',	#"Business revenue\n (beneficiary,\n monthly, USD)" 
  "ani_ben_dum", 		#"Benef. owns\n livestock\n \{0,1\}"
  "ani_contr_ben_dum", #"Benef. controls\n livestock\n revenue \{0,1\}"
  "sleep_prod_dum"	#"Benef. traveled\n for work\n \{0,1\}"
)


#----------------------------------------
# Heterogeneity Variables
#----------------------------------------
lst_het_var <- c(
  #"het_save_share",           # Share of savings controlled by partner
  "het_ctrl_earn_index",      # Heterogeneity in earnings control index
  "het_ctrl_hh_index",        # Heterogeneity in HH decision control
  "het_intrahh_index"         # Heterogeneity in intra-HH dynamics
)


# Define the two treatment variables 
treatment_vars=c("treatment_csh_trnsfr","treatment_pi","treatment_pi_pool")
```

<!---BLOCK_TOC--->


<!---BLOCK_LANDSCAPE_START--->
\newpage
# Summary

**Key Takeaways**:


# Mechanism

## Economic Security & Emotional Well-being

Cash reduces poverty stress and improve emotional well-being.
Impact: generally reduces IPV.

```{r}

######################## Fist estimate ##########################################
####################### Household level
# Create a data frame of results examining heterogeneous treatment effects
# across different economic IPV outcomes, treatment variables, and heterogeneity dimensions
mainResults_mech_hh <- map_dfr(revenue_consum_vars_hh, function(depvar) {
 
   # For each heterogeneity variable...
  tempResults1 <- map_dfr(lst_het_var, function(het_var) { 
  
    # For each treatment variable...
    tempResults2 <- map_dfr(treatment_vars, function(treat_var) {

      bind_rows(
        # Get estimates for heterogeneous treatment effects using the specified model
        getEstimate_mechanism(depvar, treat_var, het_var, control_vars, strata_vars, cluster_vars, followup_MRT_hh) %>%
          # Add columns identifying which variables were used in this iteration
          mutate(depvar = depvar, outcome = depvar, treat_var = treat_var, het_var = het_var)
        )
    })
  })
})

####################### Ben
# Create a data frame of results examining heterogeneous treatment effects
# across different economic IPV outcomes, treatment variables, and heterogeneity dimensions
mainResults_mech_ben <- map_dfr(revenue_consum_vars_ben, function(depvar) {
 
   # For each heterogeneity variable...
  tempResults1 <- map_dfr(lst_het_var, function(het_var) { 
  
    # For each treatment variable...
    tempResults2 <- map_dfr(treatment_vars, function(treat_var) {

      bind_rows(
        # Get estimates for heterogeneous treatment effects using the specified model
        getEstimate_mechanism(depvar, treat_var, het_var, control_vars, strata_vars, cluster_vars, followup_MRT_hh) %>%
          # Add columns identifying which variables were used in this iteration
          mutate(depvar = depvar, outcome = depvar, treat_var = treat_var, het_var = het_var)
        )
    })
  })
})



```

### Control over earnings

#### Household level
```{r}

# Extract results for the outcome variable 

curr_het_var_lab <- c("Earn. cntrl (high)")
curr_het_var <- c("het_ctrl_earn_index")

tbl <- getTable1_het(curr_het_var_lab, curr_het_var, revenue_consum_vars_hh, mainResults_mech_hh)
tbl
```

#### Ben level
```{r}

# Extract results for the outcome variable 

curr_het_var_lab <- c("Earn. cntrl (high)")
curr_het_var <- c("het_ctrl_earn_index")

tbl <- getTable2_het(curr_het_var_lab, curr_het_var, revenue_consum_vars_ben, mainResults_mech_ben)
tbl
```

### Control over hh. resources

#### Household level
```{r}

# Extract results for the outcome variable 

curr_het_var_lab <- c("Cntrl hh. res. (high)")
curr_het_var <- c("het_ctrl_hh_index")

tbl <- getTable1_het(curr_het_var_lab, curr_het_var, revenue_consum_vars_hh, mainResults_mech_hh)
tbl
```

#### Ben level
```{r}
tbl <- getTable2_het(curr_het_var_lab, curr_het_var, revenue_consum_vars_ben, mainResults_mech_ben)
tbl
```


### Intra-household dynamics 
#### Household level
```{r}

# Extract results for the outcome variable 

curr_het_var_lab <- c("Intra-hh. dyn. (high)")
curr_het_var <- c("het_intrahh_index")
tbl <- getTable1_het(curr_het_var_lab, curr_het_var, revenue_consum_vars_hh, mainResults_mech_hh)
# Print the final table
tbl
```

#### Ben level

```{r}
tbl <- getTable2_het(curr_het_var_lab, curr_het_var, revenue_consum_vars_ben, mainResults_mech_ben)
tbl
```

## Intra-household Conflict

```{r}
####################### Ben
# Create a data frame of results examining heterogeneous treatment effects
# across different economic IPV outcomes, treatment variables, and heterogeneity dimensions
mainResults_mech_ben <- map_dfr(intra_hh_vars, function(depvar) {
 
   # For each heterogeneity variable...
  tempResults1 <- map_dfr(lst_het_var, function(het_var) { 
  
    # For each treatment variable...
    tempResults2 <- map_dfr(treatment_vars, function(treat_var) {

      bind_rows(
        # Get estimates for heterogeneous treatment effects using the specified model
        getEstimate_mechanism(depvar, treat_var, het_var, control_vars, strata_vars, cluster_vars, followup_MRT_hh) %>%
          # Add columns identifying which variables were used in this iteration
          mutate(depvar = depvar, outcome = depvar, treat_var = treat_var, het_var = het_var)
        )
    })
  })
})


```

### Main indexes
#### Control over earnings

```{r}

# Extract results for the outcome variable 

curr_het_var_lab <- c("Earn. cntrl (high)")
curr_het_var <- c("het_ctrl_earn_index")

tbl <- getTable3_het(curr_het_var_lab, curr_het_var, intra_hh_vars, mainResults_mech_ben)
# Print the final table
tbl

```


#### Control over hh. resources

```{r}
# Extract results for the outcome variable 
curr_het_var_lab <- c("Cntrl hh. res. (high)")
curr_het_var <- c("het_ctrl_hh_index")

# Generate tables
tbl <- getTable3_het(curr_het_var_lab, curr_het_var, intra_hh_vars, mainResults_mech_ben)
tbl

```


#### Intra-household dynamics 

```{r}
# Extract results for the outcome variable 

curr_het_var_lab <- c("Intra-hh. dyn. (high)")
curr_het_var <- c("het_intrahh_index")

tbl <- getTable3_het(curr_het_var_lab, curr_het_var, intra_hh_vars, mainResults_mech_ben)
tbl
```

### Indexes components

```{r}
####################### Ben
# Create a data frame of results examining heterogeneous treatment effects
# across different dimention of intrahh index
mainResults_mech_intrah <- map_dfr(intra_hh_index_components_vars, function(depvar) {
 
   # For each heterogeneity variable...
  tempResults1 <- map_dfr(lst_het_var, function(het_var) { 
  
    # For each treatment variable...
    tempResults2 <- map_dfr(treatment_vars, function(treat_var) {

      bind_rows(
        # Get estimates for heterogeneous treatment effects using the specified model
        getEstimate_mechanism(depvar, treat_var, het_var, control_vars, strata_vars, cluster_vars, followup_MRT_hh) %>%
          # Add columns identifying which variables were used in this iteration
          mutate(depvar = depvar, outcome = depvar, treat_var = treat_var, het_var = het_var)
        )
    })
  })
})

# Violence perception index
mainResults_mech_violence <- map_dfr(violence_prcptn_index_components_vars, function(depvar) {
 
   # For each heterogeneity variable...
  tempResults1 <- map_dfr(lst_het_var, function(het_var) { 
  
    # For each treatment variable...
    tempResults2 <- map_dfr(treatment_vars, function(treat_var) {

      bind_rows(
        # Get estimates for heterogeneous treatment effects using the specified model
        getEstimate_mechanism(depvar, treat_var, het_var, control_vars, strata_vars, cluster_vars, followup_MRT_hh) %>%
          # Add columns identifying which variables were used in this iteration
          mutate(depvar = depvar, outcome = depvar, treat_var = treat_var, het_var = het_var)
        )
    })
  })
})


# Violence perception index
mainResults_mech_gender <- map_dfr(gender_attitudes_index_components_vars, function(depvar) {
 
   # For each heterogeneity variable...
  tempResults1 <- map_dfr(lst_het_var, function(het_var) { 
  
    # For each treatment variable...
    tempResults2 <- map_dfr(treatment_vars, function(treat_var) {

      bind_rows(
        # Get estimates for heterogeneous treatment effects using the specified model
        getEstimate_mechanism(depvar, treat_var, het_var, control_vars, strata_vars, cluster_vars, followup_MRT_hh) %>%
          # Add columns identifying which variables were used in this iteration
          mutate(depvar = depvar, outcome = depvar, treat_var = treat_var, het_var = het_var)
        )
    })
  })
})

# Social norm index
mainResults_mech_socialnorm <- map_dfr(social_norm_index_components_vars, function(depvar) {
 
   # For each heterogeneity variable...
  tempResults1 <- map_dfr(lst_het_var, function(het_var) { 
  
    # For each treatment variable...
    tempResults2 <- map_dfr(treatment_vars, function(treat_var) {

      bind_rows(
        # Get estimates for heterogeneous treatment effects using the specified model
        getEstimate_mechanism(depvar, treat_var, het_var, control_vars, strata_vars, cluster_vars, followup_MRT_hh) %>%
          # Add columns identifying which variables were used in this iteration
          mutate(depvar = depvar, outcome = depvar, treat_var = treat_var, het_var = het_var)
        )
    })
  })
})

```

#### Intra-household index components
##### Control over earnings

```{r}

# Extract results for the outcome variable 

curr_het_var_lab <- c("Earn. cntrl (high)")
curr_het_var <- c("het_ctrl_earn_index")

# Generate tables
tbl <- getTable3_het_intra(curr_het_var_lab, curr_het_var, intra_hh_index_components_vars, mainResults_mech_intrah)
tbl

```


##### Control over hh. resources

```{r}
# Extract results for the outcome variable 
curr_het_var_lab <- c("Cntrl hh. res. (high)")
curr_het_var <- c("het_ctrl_hh_index")

# Generate tables
tbl <- tbl <- getTable3_het_intra(curr_het_var_lab, curr_het_var, intra_hh_index_components_vars, mainResults_mech_intrah)
tbl

```


##### Intra-household dynamics 

```{r}
# Extract results for the outcome variable 
curr_het_var_lab <- c("Intra-hh. dyn. (high)")
curr_het_var <- c("het_intrahh_index")

# Generate tables
tbl <- tbl <- getTable3_het_intra(curr_het_var_lab, curr_het_var, intra_hh_index_components_vars, mainResults_mech_intrah)
tbl
```


#### Violence perception index components
##### Control over earnings

```{r}

# Extract results for the outcome variable 
curr_het_var_lab <- c("Earn. cntrl (high)")
curr_het_var <- c("het_ctrl_earn_index")

# Generate tables
tbl <- getTable3_het_violence(curr_het_var_lab, curr_het_var, violence_prcptn_index_components_vars, mainResults_mech_violence)
tbl

```


##### Control over hh. resources

```{r}
# Extract results for the outcome variable 
curr_het_var_lab <- c("Cntrl hh. res. (high)")
curr_het_var <- c("het_ctrl_hh_index")

# Generate tables
tbl <- getTable3_het_violence(curr_het_var_lab, curr_het_var, violence_prcptn_index_components_vars, mainResults_mech_violence)
tbl

```


##### Intra-household dynamics 

```{r}
# Extract results for the outcome variable 
curr_het_var_lab <- c("Intra-hh. dyn. (high)")
curr_het_var <- c("het_intrahh_index")

# Generate tables
tbl <- getTable3_het_violence(curr_het_var_lab, curr_het_var, violence_prcptn_index_components_vars, mainResults_mech_violence)
tbl
```


#### Gender attitude index components
##### Control over earnings

```{r}

# Extract results for the outcome variable 
curr_het_var_lab <- c("Earn. cntrl (high)")
curr_het_var <- c("het_ctrl_earn_index")

# Generate tables
tbl <- getTable3_het_gender(curr_het_var_lab, curr_het_var, gender_attitudes_index_components_vars, mainResults_mech_gender)
tbl

```


##### Control over hh. resources

```{r}
# Extract results for the outcome variable 
curr_het_var_lab <- c("Cntrl hh. res. (high)")
curr_het_var <- c("het_ctrl_hh_index")

# Generate tables
tbl <- getTable3_het_gender(curr_het_var_lab, curr_het_var, gender_attitudes_index_components_vars, mainResults_mech_gender)
tbl

```


##### Intra-household dynamics 

```{r}
# Extract results for the outcome variable 
curr_het_var_lab <- c("Intra-hh. dyn. (high)")
curr_het_var <- c("het_intrahh_index")

# Generate tables
tbl <- getTable3_het_gender(curr_het_var_lab, curr_het_var, gender_attitudes_index_components_vars, mainResults_mech_gender)
tbl
```


#### Social norm index components
##### Control over earnings

```{r}

# Extract results for the outcome variable 
curr_het_var_lab <- c("Earn. cntrl (high)")
curr_het_var <- c("het_ctrl_earn_index")

# Generate tables
tbl <- getTable3_het_socialnorm(curr_het_var_lab, curr_het_var, social_norm_index_components_vars, mainResults_mech_socialnorm)
tbl

```


##### Control over hh. resources

```{r}
# Extract results for the outcome variable 
curr_het_var_lab <- c("Cntrl hh. res. (high)")
curr_het_var <- c("het_ctrl_hh_index")

# Generate tables
tbl <- getTable3_het_socialnorm(curr_het_var_lab, curr_het_var, social_norm_index_components_vars, mainResults_mech_socialnorm)
tbl

```


##### Intra-household dynamics 

```{r}
# Extract results for the outcome variable 
curr_het_var_lab <- c("Intra-hh. dyn. (high)")
curr_het_var <- c("het_intrahh_index")

# Generate tables
tbl <- getTable3_het_socialnorm(curr_het_var_lab, curr_het_var, social_norm_index_components_vars, mainResults_mech_socialnorm)
tbl
```


## Women’s bargaining power
### Decision making

```{r}
####################### Ben
# Create a data frame of results examining heterogeneous treatment effects
# across different economic IPV outcomes, treatment variables, and heterogeneity dimensions
mainResults_mech_ben <- map_dfr(dec_making, function(depvar) {
 
   # For each heterogeneity variable...
  tempResults1 <- map_dfr(lst_het_var, function(het_var) { 
  
    # For each treatment variable...
    tempResults2 <- map_dfr(treatment_vars, function(treat_var) {

      bind_rows(
        # Get estimates for heterogeneous treatment effects using the specified model
        getEstimate_mechanism(depvar, treat_var, het_var, control_vars, strata_vars, cluster_vars, followup_MRT_hh) %>%
          # Add columns identifying which variables were used in this iteration
          mutate(depvar = depvar, outcome = depvar, treat_var = treat_var, het_var = het_var)
        )
    })
  })
})

```


#### Control over earnings

```{r}

# Extract results for the outcome variable 
curr_het_var_lab <- c("Earn. cntrl (high)")
curr_het_var <- c("het_ctrl_earn_index")

tbl <- getTable4_het(curr_het_var_lab, curr_het_var, dec_making, mainResults_mech_hh)
tbl
```

#### Control over hh. resources

```{r}

# Extract results for the outcome variable 
curr_het_var_lab <- c("Cntrl hh. res. (high)")
curr_het_var <- c("het_ctrl_hh_index")

tbl <- getTable4_het(curr_het_var_lab, curr_het_var, dec_making, mainResults_mech_hh)
tbl
```


#### Intra-household dynamics 

```{r}

curr_het_var_lab <- c("Intra-hh. dyn. (high)")
curr_het_var <- c("het_intrahh_index")

tbl <- getTable4_het(curr_het_var_lab, curr_het_var, dec_making, mainResults_mech_hh)
tbl
```

### Empowerment 

```{r}

####################### Ben
# Create a data frame of results examining heterogeneous treatment effects
# across different economic IPV outcomes, treatment variables, and heterogeneity dimensions
mainResults_mech_ben <- map_dfr(empowerment, function(depvar) {
 
   # For each heterogeneity variable...
  tempResults1 <- map_dfr(lst_het_var, function(het_var) { 
  
    # For each treatment variable...
    tempResults2 <- map_dfr(treatment_vars, function(treat_var) {

      bind_rows(
        # Get estimates for heterogeneous treatment effects using the specified model
        getEstimate_mechanism(depvar, treat_var, het_var, control_vars, strata_vars, cluster_vars, followup_MRT_hh) %>%
          # Add columns identifying which variables were used in this iteration
          mutate(depvar = depvar, outcome = depvar, treat_var = treat_var, het_var = het_var)
        )
    })
  })
})

```



#### Control over earnings

```{r}

# Extract results for the outcome variable 
curr_het_var_lab <- c("Earn. cntrl (high)")
curr_het_var <- c("het_ctrl_earn_index")

tbl <- getTable7_het(curr_het_var_lab, curr_het_var, empowerment, mainResults_mech_ben)
tbl
```

#### Control over hh. resources

```{r}

# Extract results for the outcome variable 
curr_het_var_lab <- c("Cntrl hh. res. (high)")
curr_het_var <- c("het_ctrl_hh_index")

tbl <- getTable7_het(curr_het_var_lab, curr_het_var, empowerment, mainResults_mech_ben)
tbl
```


#### Intra-household dynamics 

```{r}

curr_het_var_lab <- c("Intra-hh. dyn. (high)")
curr_het_var <- c("het_intrahh_index")

tbl <- getTable7_het(curr_het_var_lab, curr_het_var, empowerment, mainResults_mech_ben)
tbl
```


## Intensive time use
### Grouping time use variables

```{r}


in_house_chores <- c(
  "time_wk_ben_water",     # fetching water
  "time_wk_ben_cook",      # cooking
  "time_wk_ben_clean",     # cleaning
  "time_wk_ben_laundry",   # laundry
  "time_wk_ben_shop",      # shopping
  "time_wk_ben_child",        # childcare
  "time_wk_ben_firewood",  # collecting firewood
  "time_wk_ben_handicap"      # helping disabled relatives
)

market_income <- c(
  "time_wk_ben_nonag",     # non-agricultural business
  "time_wk_ben_ag",        # agriculture
  "time_wk_ben_liv"        # livestock
)


leisure_time <- c(
  "time_wk_ben_study_coran",  # studying Quran
  "time_wk_ben_study_trad",   # traditional study
  "time_wk_ben_family",          # time with friends/family
  "time_wk_ben_radio",           # listening to radio
  "time_wk_ben_rest",            # resting
  "time_wk_ben_pray"             # praying
)

time_use_group <- c("tot_time_in_house_chores","tot_time_market_income","tot_time_leisure","tot_time_other")

followup_MRT_hh <- followup_MRT_hh %>%
  mutate(tot_time_in_house_chores = apply(select(., in_house_chores), 1, sum, na.rm = TRUE)) %>% 
  mutate(tot_time_market_income = apply(select(., market_income), 1, sum, na.rm = TRUE)) %>% 
  mutate(tot_time_leisure = apply(select(., leisure_time), 1, sum, na.rm = TRUE))%>% 
  mutate(tot_time_other = 10080 - (tot_time_in_house_chores + tot_time_market_income + tot_time_leisure))

followup_MRT_hh_control <- followup_MRT_hh_control %>%
  mutate(tot_time_in_house_chores = apply(select(., in_house_chores), 1, sum, na.rm = TRUE)) %>% 
  mutate(tot_time_market_income = apply(select(., market_income), 1, sum, na.rm = TRUE)) %>% 
  mutate(tot_time_leisure = apply(select(., leisure_time), 1, sum, na.rm = TRUE))%>% 
  mutate(tot_time_other = 10080 - (tot_time_in_house_chores + tot_time_market_income + tot_time_leisure))

####################### Ben
# Create a data frame of results examining heterogeneous treatment effects
# across different economic IPV outcomes, treatment variables, and heterogeneity dimensions
mainResults_mech_ben <- map_dfr(time_use_group, function(depvar) {
 
   # For each heterogeneity variable...
  tempResults1 <- map_dfr(lst_het_var, function(het_var) { 
  
    # For each treatment variable...
    tempResults2 <- map_dfr(treatment_vars, function(treat_var) {

      bind_rows(
        # Get estimates for heterogeneous treatment effects using the specified model
        getEstimate_mechanism(depvar, treat_var, het_var, control_vars, strata_vars, cluster_vars, followup_MRT_hh) %>%
          # Add columns identifying which variables were used in this iteration
          mutate(depvar = depvar, outcome = depvar, treat_var = treat_var, het_var = het_var)
        )
    })
  })
})

```



#### Control over earnings

```{r}

# Extract results for the outcome variable 
curr_het_var_lab <- c("Earn. cntrl (high)")
curr_het_var <- c("het_ctrl_earn_index")

tbl <- getTable5_het(curr_het_var_lab, curr_het_var, time_use_group, mainResults_mech_ben)
tbl

```



#### Control over hh. resources

```{r}

# Extract results for the outcome variable 
curr_het_var_lab <- c("Cntrl hh. res. (high)")
curr_het_var <- c("het_ctrl_hh_index")

tbl <- getTable5_het(curr_het_var_lab, curr_het_var, time_use_group, mainResults_mech_ben)
tbl
```

#### Intra-household dynamics 

```{r}

curr_het_var_lab <- c("Intra-hh. dyn. (high)")
curr_het_var <- c("het_intrahh_index")

tbl <- getTable5_het(curr_het_var_lab, curr_het_var, time_use_group, mainResults_mech_ben)
tbl
```

### All variables
```{r}
####################### Ben
# Create a data frame of results examining heterogeneous treatment effects
# across different economic IPV outcomes, treatment variables, and heterogeneity dimensions
mainResults_mech_ben <- map_dfr(time_use_int, function(depvar) {
 
   # For each heterogeneity variable...
  tempResults1 <- map_dfr(lst_het_var, function(het_var) { 
  
    # For each treatment variable...
    tempResults2 <- map_dfr(treatment_vars, function(treat_var) {

      bind_rows(
        # Get estimates for heterogeneous treatment effects using the specified model
        getEstimate_mechanism(depvar, treat_var, het_var, control_vars, strata_vars, cluster_vars, followup_MRT_hh) %>%
          # Add columns identifying which variables were used in this iteration
          mutate(depvar = depvar, outcome = depvar, treat_var = treat_var, het_var = het_var)
        )
    })
  })
})

```


#### Control over earnings

```{r}

# Extract results for the outcome variable 
curr_het_var_lab <- c("Earn. cntrl (high)")
curr_het_var <- c("het_ctrl_earn_index")

tbl <- getTable6_het(curr_het_var_lab, curr_het_var, time_use_int, mainResults_mech_ben)
tbl
```


#### Control over hh. resources

```{r}

# Extract results for the outcome variable 
curr_het_var_lab <- c("Cntrl hh. res. (high)")
curr_het_var <- c("het_ctrl_hh_index")

tbl <- getTable6_het(curr_het_var_lab, curr_het_var, time_use_int, mainResults_mech_ben)
tbl
```

#### Intra-household dynamics 

```{r}

curr_het_var_lab <- c("Intra-hh. dyn. (high)")
curr_het_var <- c("het_intrahh_index")

tbl <- getTable6_het(curr_het_var_lab, curr_het_var, time_use_int, mainResults_mech_ben)
tbl
```


```{r}
# remove data to free space
rm(list = ls())
```
