---
title: "Cash Plus, Safety Plus? Intimate Partner Violence and Economic Inclusion in Mauritania"
subtitle: "Mechanism"
author: "IBRAHIM KASSOUM Habibou"
date: '`r format (Sys.Date(), "%d %B %Y")`'
output: 
  officedown::rdocx_document:
    mapstyles:
      Normal: ['First Paragraph']
    number_sections: true
    fig_caption: true
---


```{r setup, include=FALSE}
# Set random seed for reproducibility
set.seed(7654)

# Set number of decimal places to display
options(digits = 3)

# Configure knitr chunk options:
knitr::opts_chunk$set(
 echo = FALSE,          # Don't show R code in output
 message = FALSE,       # Don't show messages
 warning = FALSE,       # Don't show warnings
 cache = FALSE,         # Don't cache results
 fig.align = 'center',  # Center figures
 fig.width = 6.3,         # Figure width in inches
 fig.height= 7,          # Figure height in inches
 fig.asp = 0.8,       # Figure aspect ratio (golden ratio)
 fig.show = "hold"      # Hold multiple plots until end of chunk
)

# Set dplyr print options to show 6 rows max
options(dplyr.print_min = 6, dplyr.print_max = 6)

# Set max vector size
mem.maxVSize(vsize = Inf)
# Sometimes temporary files accumulate and cause issues. You can clear them manually or use:
#unlink(tempdir(), recursive = TRUE)
```


```{r, include=FALSE, results='hide', echo=FALSE}

######################## Importing library and external files ##################
### List of required packages
required_packages <- c("tidyverse", "dplyr","officedown", "officer", "gtsummary",
                       "stargazer", "lfe","labelled","car","purrr", "flextable","remotes")

### Check if packages are installed
missing_packages <- setdiff(required_packages, installed.packages()[,"Package"])

### Install missing packages
if (length(missing_packages) > 0) {
  install.packages(missing_packages)
}

### Load all packages
lapply(required_packages, library, character.only = TRUE)

# Remove all objects
rm(list = ls())

# Source functions from external file
source("functions.R")
#source("functions2.R")
#  Importing module to concatenate several model
#remotes::install_github("ChandlerLutz/starpolishr")
```



```{r echo=F}

set_gtsummary_theme(theme_gtsummary_compact())

######### Create default BioAVR table from dataframe
#
# Dependencies : dplyr, flextable, officer
# source link : https://www.r-bloggers.com/2021/11/publication-ready-tables-with-flextable-and-own-theme-in-r/
customtab_defaults <- function(){
set_flextable_defaults(font.family = "Times New Roman",
font.size = 10,
border.color = "black")
}

custom_tab <- function(df, header, footer){
flextable(df) %>%
add_header_lines(header) %>%
add_footer_lines(footer) %>%
bold(i = 1, part = "header") %>%
hline_top(part = "header",
border = fp_border(color = "white",
width = 3,
style = "solid")) %>%
hline(i = 1,
part = "header",
border = fp_border(color = "black",
width = 0.25,
style = "solid")) %>%
hline_top(part = "body",
border = fp_border(color = "black",
width = 0.25,
style = "solid")) %>%
hline_bottom(part = "body",
border = fp_border(color = "black",
width = 0.25,
style = "solid")) %>%
hline_bottom(part = "footer",
border = fp_border(color = "black",
width = 0.25,
style = "solid")) %>%
border_inner_h(part = "body",
border = fp_border(color = "black",
width = 0.25,
style = "dotted")) %>%
autofit(part = "body") %>%
bg(part = "body", bg = "white") %>%
align(part = "all", align = "center") %>%
align(j = 1, part = "all", align = "left")
}
```


```{r}

######################## Loading the datasets ##################################
# Read the file containing the global dataframe into followup_ipv_MRT_hh

followup_ipv_MRT_hh <- readRDS(paste0(getwd(),"/output/data/followup_ipv_MRT_hh.rds"))

# Creating some variables at partner level
followup_ipv_MRT_hh <- followup_ipv_MRT_hh %>% 
  mutate(rev_sum_prt_wemp_98 = rev_sum_hh_wemp_98 - rev_sum_ben_wemp_98,  
         tot_prt_rev12_98_ppp = tot_hh_rev12_98_ppp - tot_ben_rev12_98_ppp,   
         tot_emp_2rev12_prt_98_ppp = tot_emp_2rev12_hh_98_ppp - tot_emp_2rev12_ben_98_ppp,  
         tot_ani_prt_contr_98_ppp = tot_ani_hh_contr_98_ppp - tot_ani_ben_contr_98_ppp)
# Convert treatment variables from numeric to factor variables for both datasets
# This is useful for regression analysis and plotting as factors are treated as categorical variables
 # Convert PM treatment to factor
followup_ipv_MRT_hh$treatment_pi <- haven::as_factor(followup_ipv_MRT_hh$treatment_pi)

# Convert cash transfer treatment to factor
followup_ipv_MRT_hh$treatment_csh_trnsfr <- haven::as_factor(followup_ipv_MRT_hh$treatment_csh_trnsfr)

followup_ipv_MRT_hh_control_pi <- followup_ipv_MRT_hh %>% filter(treatment_pi=="Control") %>%
      filter(reg_hh_pi_mrt==1)

followup_ipv_MRT_hh_control_csh_trnsfr <- followup_ipv_MRT_hh %>% filter(treatment_csh_trnsfr=="Control") %>% 
      filter(reg_hh_csh_mrt==1)


# Define controls variables for the regression 
# control_vars = c("hhh_fem_bl",
#             "mem_n_bl",
#             "same_cb",
#             "pben_handicap",
#             "hhh_poly",
#             "pben_poly",
#             "hhh_age",
#             "pben_age",
#             "age_gap",
#             "hhh_edu",
#             "pben_edu",
#             "hhh_lit",
#             "pben_lit")

# Define controls variables for the regression 
# control_vars = c(
#                 "pben_handicap_bl",
#                 "hhh_prim_bl",
#                 "pben_prim_bl",
#                 "het_nbr_elder",
#                 "hh_has_kid",
#                 "het_wtht_adult_mal",
#                 "hhh_fem_bl",
#                 "same_cb",
#                 "pben_age_bl",
#                 "age_gap",
#                 "hhh_edu_bl",
#                 "pben_edu_bl",
#                 "hhh_lit_bl",
#                 "pben_lit_bl"
#             )

  # PRIORITY 1: Imbalanced variables that MUST be controlled
  # These showed statistical differences at baseline
  control_vars = c(
    # Demographics with imbalance
    #"age_gap",              # Significant in (2)-(3), Joint F-test
    
    
    # Elder/children with imbalance
    "nbr_elder",            # Significant in (1)-(2), (2)-(3), JoiÒnt F-test
    "het_nbr_elder",        # Significant in (1)-(2), (2)-(3), Joint F-test
    "shr_elder",            # Significant in (1)-(2), (2)-(3), Joint F-test
    
    # Education with imbalance
    "hhh_prim_bl",          # Significant in (1)-(4), (3)-(4), Joint F-test
    "pben_lit_bl",          # Significant in (1)-(2), (1)-(4), (2)-(3), (3)-(4), Joint F-test
    
    
    # Economic with imbalance
   "tot_emp_2rev12_ben_98_ppp_bl", # Significant in (1)-(2), (1)-(4), (2)-(4), Joint F-test
    
    # Business with imbalance
    "bus2_within_12_dum_ben_bl" # Significant in (1)-(3), (1)-(4), (2)-(4), Joint F-test, Pooled
  )
# Define strata variables: strata
strata_vars <- c("strata") 

# Define cluster variables 
cluster_vars <- c("cluster")

# PRIORITY 1: Imbalanced variables that MUST be controlled
# These showed statistical differences at baseline
  # control_vars = c(
  #   # Elder/children with imbalance
  #   "nbr_elder",            # Significant in (1)-(2), (2)-(3), JoiÒnt F-test
  #   "het_nbr_elder",        # Significant in (1)-(2), (2)-(3), Joint F-test
  #   "shr_elder",            # Significant in (1)-(2), (2)-(3), Joint F-test
  #   
  #   # Education with imbalance
  #   "hhh_prim_bl",          # Significant in (1)-(4), (3)-(4), Joint F-test
  #   "pben_lit_bl",          # Significant in (1)-(2), (1)-(4), (2)-(3), (3)-(4), Joint F-test
  #   
  #   
  #   # Economic with imbalance
  #  "tot_emp_2rev12_ben_98_ppp_bl", # Significant in (1)-(2), (1)-(4), (2)-(4), Joint F-test
  #   
  #   # Business with imbalance
  #   "bus2_within_12_dum_ben_bl" # Significant in (1)-(3), (1)-(4), (2)-(4), Joint F-test, Pooled
  # )
  # 

# List of outcomes definition mechanism
#----------------------------------------
# Revenue and Consumption Outcome Variables
#----------------------------------------
revenue_consum_vars_hh <- c(
  "consum_2_day_eq_ppp",        # Consumption per capita (PPP-adjusted)
  "food_2_day_eq_ppp", 	# "Food\n consumption\n (daily, USD/adult eq.)"
  "nonfood_day_eq_ppp",	 # Non food consumption
  "eatout_day_eq_ppp",	#"Eating out\n expenditure\n (daily, USD/adult eq.)"
	"edu_day_eq_ppp", # Education expenditures
  "health_day_eq_ppp", # Health expenditures
  "cel_day_eq_ppp", # # Celebration expenditures
  "ton_or_avec_hh", # "Takes part in\n tontine/AVEC\n \{0,1\}"
  "tot_cred_out_ppp", #  "Total\n debt\n (yearly, USD)"	
  "tot_cred_amt_ppp", #  "Total\n borrowed\n (yearly, USD)"
  "gross_trans_ppp", #"Household\n Gross transfers\n (yearly, USD)"
  "saving_ppp", # Saving tot
  "FIES_rvrs_raw",            # Food Insecurity Experience Scale (reversed)
  "FCS",                      # Food Consumption Score

  # Revenue-related variables
  "rev_sum_hh_wemp_98",       # Total household revenue from work (women employment sample, 98th
  "tot_hh_rev12_98_ppp",      # Total household revenue in past 12 months (98th pctl, PPP)
  "tot_emp_2rev12_hh_98_ppp", # Total employment-related revenue over 12 months (winsorized 98th pctl)
  "tot_ani_hh_contr_98_ppp",
  
  # Income diversification variables
  "all_income_cat",           # Number of income categories
  "all_income_div",           # Income diversification index
  "div_emp12_n"              # Number of employment sources over 12 months
)

revenue_consum_vars_ben <- c(
  # Revenue-related variables
  "rev_sum_hh_wemp_98",
  "rev_sum_ben_wemp_98",       # Total ben revenue from work (women employment sample, 98th percentile winsorized)
  "rev_sum_prt_wemp_98",
  "tot_hh_rev12_98_ppp", 
  "tot_ben_rev12_98_ppp",      # Total ben revenue in past 12 months (98th pctl, PPP)
  "tot_prt_rev12_98_ppp",
  "tot_emp_2rev12_hh_98_ppp",
  "tot_emp_2rev12_ben_98_ppp", # Total ben employment-related revenue over 12 months (winsorized 98th pctl)
  "tot_emp_2rev12_prt_98_ppp",
  "tot_ani_hh_contr_98_ppp",
  "tot_ani_ben_contr_98_ppp",
  "tot_ani_prt_contr_98_ppp"
)


#----------------------------------------
# Intra-household dynamics index
#----------------------------------------
intra_hh_vars <- c(
  "intrahh_vars_index",       # Composite index of intra-household dynamics
  "dom_relation_index",       # Index of domestic relationship/violence perception
  "gender_attitudes_index"    # Index measuring gender role attitudes
)


#----------------------------------------
# Decision-Making and Control Over Income
#----------------------------------------
dec_making <- c(
  "ctrl_hh_index",            # Index of control over household decisions
  "ctrl_earn_index",          # Index of control over earnings
  "dec_pow_earn", "dec_could_earn",      # Power/capacity to earn
  "dec_pow_ag", "dec_pow_liv", "dec_pow_bus",  # Power in Economic sectors
  "dec_pow_spend", "dec_could_spend", "dec_pow_large", "dec_could_large",
  "dec_pow_fert", "dec_could_fert", "dec_pow_care", "dec_could_care",
  "dec_pow_his_earn", "dec_pow_edu"
  
)


#----------------------------------------
# Intra-household Index Components
#----------------------------------------
intra_hh_index_components_vars <- c(
  "intrahh_vars_index",        # Overall intra-HH index
  "partner_vars_index",        # Partner dynamics index
  "rel_disagree",   # Relational and employment conflict indicators
  "rel_interest", "los3", 
  "hh_vars_index",             # General HH relationship index
  "los1", "tens_house",  # Loss/tension/stress indicators
  "stair_satis_today"
)


#----------------------------------------
# Intra-household Index Components
#----------------------------------------
priv_expenditures <- c(
            "male_expenditure",         # Total male expenditures
            "female_expenditure",       # Total female expenditures
            "other_expenditure"         # Other total expenditures
            )

#----------------------------------------
# Index Components: Social Norms
#----------------------------------------
social_norm_index_components_vars <- c(
  "soc_norms_index",           # Composite social norms index
  "dscrptv_norms_index",       # Descriptive norms
  "ten_support", "ten_loan", "ten_new", "ten_travel",  # Support/loan/social mobility
  "prscrptv_norms_index",      # Prescriptive norms
  "ten_mentravel_rvrs", "ten_menown_rvrs",             # Norms about men
  "ten_womentravel_rvrs", "ten_womenown_rvrs"          # Norms about women
)

#----------------------------------------
# Index Components: Gender Attitudes
#----------------------------------------
gender_attitudes_index_components_vars <- c(
  "gender_attitudes_index",    # Overall gender attitude index
  "dom_burn", "dom_kids",    # Household duties perceptions
  "ten_violen", "ten_men", "ten_boys"  # Violence/gender roles
)

#----------------------------------------
# Index Components: Perceptions of Violence
#----------------------------------------
violence_prcptn_index_components_vars <- c(
  "dom_relation_index", "ten_tension",   # Domestic tension/perceptions
  "vill_burn", "vill_kids"               # Village level violence indicators
)

#----------------------------------------
# Index Components: Control Over Earnings
#----------------------------------------
ctrl_over_earn_index_components_vars <- c(
  "ctrl_earn_index",          # Index of control over earnings
  "dec_pow_earn", "dec_could_earn",      # Power/capacity to earn
  "dec_pow_ag", "dec_pow_liv", "dec_pow_bus",  # Power in Economic sectors
  "crop_ctrl_dum", "bus2_ben_dum", "ani_ben_dum", "ani_contr_ben_dum", "sleep_prod_dum"  # Decision control variables
)

#----------------------------------------
# Index Components: Control Over Household
#----------------------------------------
ctrl_hh_index_components_vars <- c(
  "ctrl_hh_index", "dec_pow_spend", "dec_could_spend", "dec_pow_large", "dec_could_large",
  "dec_pow_fert", "dec_could_fert", "dec_pow_care", "dec_could_care",
  "dec_pow_his_earn", "dec_pow_edu"
)

#----------------------------------------
# Mental Health Index Components
#----------------------------------------
mental_health_index_components_vars <- c(
  "ment_hlth_index",           # Mental health index
  "less_depressed", "less_disability",  # Depression and disability indicators
  "stair_satis_today", "stairs_peace",  # Life satisfaction and peace of mind
  "health_ment_z"              # Z-score of mental health
)



empowerment <- c(
  "dec_could_earn", 			# decision could earn
  "tot_emp_2rev12_ben_98_ppp", 		#"Wage\n earnings\n (yearly, USD)"
	"crop_ctrl_dum", 	#"Benef. controls\n crop\n revenue \{0,1\}"
  "na_bus2_op_wn_12_ben", # No. of\n beneficiary\n businesses
  "bus2_ben_dum",	 	#"Beneficiary\n has a\n business \{0,1\}"
  "tot_busmths_uniq_ben", #No. of months benef worked last year
  "div_n_na_12_ben", # Entrepreneurial\n business types\n (yearly)
  "bus2_within_12_dum_ben",	#Beneficiary\n launched a\n business \{0,1\}				
	"bus2_abandon_24_dum_ben", # Beneficiary\n abandoned a\n business \{0,1\}
  "tot_put_1_ppp", 		#"Personnal\n savings"
  "tot_ben_rev12_98_ppp", # Business\n revenues\n (yearly, USD)    	
	"tot_ben_pro12_98_ppp", # Business\n profits\n (yearly, USD)
  "bus_assval_ben_98_ppp", # Business\n asset\n value (USD)
  "bus2_invest_ppp", # Beneficiary\n investments\n (yearly, USD)
  'tot_ben_rev30_98_ppp',	#"Business revenue\n (beneficiary,\n monthly, USD)" 
  "ani_ben_dum", 		#"Benef. owns\n livestock\n \{0,1\}"
  "ani_contr_ben_dum", #"Benef. controls\n livestock\n revenue \{0,1\}"
  "sleep_prod_dum"	#"Benef. traveled\n for work\n \{0,1\}"
)

#----------------------------------------
# Time Use Variables (hours or dummies)
#----------------------------------------
time_use_int <- c(
  # Weekly time use by activity
  "time_wk_ben_nonag",        # Time in non-ag activities
  "time_wk_ben_water",        # Time fetching water
  "time_wk_ben_cook",         # Time cooking
  "time_wk_ben_ag",           # Time in agricultural activities
  "time_wk_ben_firewood",     # Time collecting firewood
  "time_wk_ben_clean",        # Time cleaning
  "time_wk_ben_study_coran",  # Time studying the Quran
  "time_wk_ben_laundry",      # Time doing laundry
  "time_wk_ben_liv",          # Time in livestock activities
  "time_wk_ben_study_trad",   # Time in traditional study
  "time_wk_ben_shop",         # Time shopping
  "time_wk_ben_child",# Time with children and disabled relatives
  "time_wk_ben_handicap",        # Time with disabled
  "time_wk_ben_family",          # Time with friends
  "time_wk_ben_radio",           # Time listening to radio
  "time_wk_ben_rest",            # Time resting
  "time_wk_ben_study_trad",   # Time studying traditional school
  "time_wk_ben_shop",            # Time spent shopping
  "time_wk_ben_pray"            # Time praying
)



time_use_ext <- c(

  # Dummy variables indicating whether these activities were done
  "time_ben_nonag_d", "time_ben_ag_d", "time_ben_study_coran_d", 
  "time_ben_study_trad_d", "time_ben_water_d","time_ben_firewood_d", 
  "time_ben_laundry_d", "time_ben_shop_d", "time_ben_cook_d", "time_ben_clean_d",
  "time_ben_liv_d", "time_ben_child_d", "time_ben_handicap_d", "time_ben_family_d",
  "time_ben_radio_d", "time_ben_rest_d", "time_ben_study_trad_d","time_ben_shop_d",
  "time_ben_pray_d"
)

in_house_chores <- c(
  "time_wk_ben_water",     # fetching water
  "time_wk_ben_cook",      # cooking
  "time_wk_ben_clean",     # cleaning
  "time_wk_ben_laundry",   # laundry
  "time_wk_ben_shop",      # shopping
  "time_wk_ben_child",        # childcare and handicaped relatives
  "time_wk_ben_firewood",  # collecting firewood
  "time_wk_ben_handicap"      # helping disabled relatives
)

market_income <- c(
  "time_wk_ben_nonag",     # non-agricultural business
  "time_wk_ben_ag",        # agriculture
  "time_wk_ben_liv"        # livestock
)


leisure_time <- c(
  "time_wk_ben_study_coran",  # studying Quran
  "time_wk_ben_study_trad",   # traditional study
  "time_wk_ben_family",          # time with friends/family
  "time_wk_ben_radio",           # listening to radio
  "time_wk_ben_rest",            # resting
  "time_wk_ben_pray"             # praying
)

time_use_group <- c("tot_time_in_house_chores","tot_time_market_income","tot_time_leisure","tot_time_other")

followup_ipv_MRT_hh <- followup_ipv_MRT_hh %>% 
  mutate(time_wk_ben_child_handicap = time_wk_ben_child + time_wk_ben_handicap) %>%
  mutate(tot_time_in_house_chores = apply(select(., in_house_chores), 1, sum, na.rm = TRUE)) %>% 
  mutate(tot_time_market_income = apply(select(., market_income), 1, sum, na.rm = TRUE)) %>% 
  mutate(tot_time_leisure = apply(select(., leisure_time), 1, sum, na.rm = TRUE))%>% 
  mutate(tot_time_other = 10080 - (tot_time_in_house_chores + tot_time_market_income + tot_time_leisure)) 

# Control group in Main
followup_ipv_MRT_hh_control_pi <- followup_ipv_MRT_hh %>% 
  filter(treatment_pi=="Control") %>% 
  filter(reg_hh_pi_mrt==1)

followup_ipv_MRT_hh_control_csh_trnsfr <- followup_ipv_MRT_hh %>% filter(treatment_csh_trnsfr=="Control") %>% 
      filter(reg_hh_csh_mrt==1)


# Define the two treatment variables 
treatment_vars=c("treatment_csh_trnsfr","treatment_pi","treatment_pi_pool")
```

<!---BLOCK_TOC--->


<!---BLOCK_LANDSCAPE_START--->
\newpage
# Summary

**Key Takeaways**:


# Mechanism



## Mechanism 2 : Intra-household Conflict

```{r}
####################### Ben
# Create a data frame of results examining heterogeneous treatment effects
# across different economic IPV outcomes, treatment variables, and heterogeneity dimensions
mainResults_mech_ben <- map_dfr(intra_hh_vars, function(depvar) {
  
    # For each treatment variable...
    tempResults2 <- map_dfr(treatment_vars, function(treat_var) {

      bind_rows(
        # Get estimates for heterogeneous treatment effects using the specified model
        getEstimate_mechanism(depvar, treat_var, control_vars, strata_vars, cluster_vars, followup_ipv_MRT_hh) %>%
          # Add columns identifying which variables were used in this iteration
          mutate(depvar = depvar, outcome = depvar, treat_var = treat_var)
        )
  })
})


```

### Main variables
```{r}

# Extract results for the outcome variable 

  
  outcome_labels <- c(
    "Intra-household \n dynamics index",
    "Violence \n perceptions index",
    "Gender \n attitudes index"
  )
  
table_title = "Effects of the programs on Intrahousehould dynamic"
tbl <- getTable1_mech(intra_hh_vars, mainResults_mech_ben, outcome_labels, table_title)
tbl

# tbl <- getTable3_het(intra_hh_vars, mainResults_mech_ben)
# # Print the final table
# tbl

```



### Indexes components

```{r}
####################### Ben
# Create a data frame of results examining heterogeneous treatment effects
# across different dimention of intrahh index
mainResults_mech_intrah <- map_dfr(intra_hh_index_components_vars, function(depvar) {

  
    # For each treatment variable...
    tempResults2 <- map_dfr(treatment_vars, function(treat_var) {

      bind_rows(
        # Get estimates for heterogeneous treatment effects using the specified model
        getEstimate_mechanism(depvar, treat_var, control_vars, strata_vars, cluster_vars, followup_ipv_MRT_hh) %>%
          # Add columns identifying which variables were used in this iteration
          mutate(depvar = depvar, outcome = depvar, treat_var = treat_var)
        )
    })
})

# Violence perception index
mainResults_mech_violence <- map_dfr(violence_prcptn_index_components_vars, function(depvar) {
 
  
    # For each treatment variable...
    tempResults2 <- map_dfr(treatment_vars, function(treat_var) {

      bind_rows(
        # Get estimates for heterogeneous treatment effects using the specified model
        getEstimate_mechanism(depvar, treat_var, control_vars, strata_vars, cluster_vars, followup_ipv_MRT_hh) %>%
          # Add columns identifying which variables were used in this iteration
          mutate(depvar = depvar, outcome = depvar, treat_var = treat_var)
        )
  })
})


# Violence perception index
mainResults_mech_gender <- map_dfr(gender_attitudes_index_components_vars, function(depvar) {
 
  
    # For each treatment variable...
    tempResults2 <- map_dfr(treatment_vars, function(treat_var) {

      bind_rows(
        # Get estimates for heterogeneous treatment effects using the specified model
        getEstimate_mechanism(depvar, treat_var, control_vars, strata_vars, cluster_vars, followup_ipv_MRT_hh) %>%
          # Add columns identifying which variables were used in this iteration
          mutate(depvar = depvar, outcome = depvar, treat_var = treat_var)
        )
  })
})

# Social norm index
mainResults_mech_socialnorm <- map_dfr(social_norm_index_components_vars, function(depvar) {

  
    # For each treatment variable...
    tempResults2 <- map_dfr(treatment_vars, function(treat_var) {

      bind_rows(
        # Get estimates for heterogeneous treatment effects using the specified model
        getEstimate_mechanism(depvar, treat_var, control_vars, strata_vars, cluster_vars, followup_ipv_MRT_hh) %>%
          # Add columns identifying which variables were used in this iteration
          mutate(depvar = depvar, outcome = depvar, treat_var = treat_var)
        )
  })
})


# Social norm index
mainResults_mech_private <- map_dfr(priv_expenditures, function(depvar) {

  
    # For each treatment variable...
    tempResults2 <- map_dfr(treatment_vars, function(treat_var) {

      bind_rows(
        # Get estimates for heterogeneous treatment effects using the specified model
        getEstimate_mechanism(depvar, treat_var, control_vars, strata_vars, cluster_vars, followup_ipv_MRT_hh) %>%
          # Add columns identifying which variables were used in this iteration
          mutate(depvar = depvar, outcome = depvar, treat_var = treat_var)
        )
  })
})


```

### Intra-household dynamics index and components
```{r}
# Extract results for the outcome variable 

outcome_labels <- c(
  "Intra-household \n dynamics \n index",
  "Partner \n dynamics \n index",
  "Comfortable \n disagreeing with \n partner (1-4)",
  "Trusts\n partner\n (1-4)",
  "Partner\n inclusiveness\n (1-4)",
  "Household \n dynamics \n index",
  "Household\n inclusiveness\n (1-4)",
  "Household\n tensions\n frequent (1-4)",
  "Relationship \n satisfaction \n (1-10)"
  )


  
table_title = "Effects of the programs on Household tension"
tbl <- getTable1_mech(intra_hh_index_components_vars, mainResults_mech_intrah, outcome_labels, table_title)
tbl
```


#### Social norm index and components
```{r}

outcome_labels <- c(
    "Social\n norms\n index",
    "Descriptive\n norms\n index",
    "Know women\n travel freely\n (0-10)",
    "Know\n women\n with loans (0-10)",
    "Know women\n who started\n activities (0-10)",
    "Know women\n travel freely \n (0-10)",
    "Prescriptive\n norms\n index",
    "No. men who think\n women shd travel\n freely (0-10)",
    "No. men who think\n women shd have\n own work (0-10)",
    "No. women who think\n women shd travel\n freely (0-10)",
    "No. women who think\n women shd have\n own work (0-10)"
  )

table_title = "Effects of the programs on Norms"

tbl <- getTable1_mech(social_norm_index_components_vars, mainResults_mech_socialnorm, outcome_labels, table_title)
tbl

# # Generate tables
# tbl <- getTable3_het_intra(intra_hh_index_components_vars, mainResults_mech_intrah)
# tbl
```


#### Gender attitudes index 

```{r}

outcome_labels <- c(
  "Gender\n attitudes\n index",
  # Individual component variables:
  "Food violence \n is OK (0,1)",
  "Children violence \n is OK (0,1)",
  "Should tolerate \n violence (1-4)",
  "Only men should \n work (1-4)",
  "Should school \n girls (1-4)"
  )
  
table_title = "Effects of the programs on Gender attitudes and components"
tbl <- getTable1_mech(gender_attitudes_index_components_vars, mainResults_mech_gender, outcome_labels, table_title)
tbl

# Generate tables
# tbl <- getTable3_het_violence(violence_prcptn_index_components_vars, mainResults_mech_violence)
# tbl

```




#### Violence perception index components

```{r}

outcome_labels <- c(
  "Violence\n perceptions\n index",
  "HH tension \n (out of 10 women)",
  "Village: beating \n OK if burns \n  food (0,1)",
  "Village: beating \n OK if neglects \n kids (0,1)"
  )
  
table_title = "Effects of the programs on Violence perceptions and components"

tbl <- getTable1_mech(violence_prcptn_index_components_vars, mainResults_mech_violence, outcome_labels, table_title)
tbl

# Generate tables
# tbl <- getTable3_het_gender(gender_attitudes_index_components_vars, mainResults_mech_gender)
# tbl

```



#### Social norm index components

```{r}


outcome_labels <- c(
  "Social\n norms\n index",
  "Descriptive\n norms\n index",
  "Know women\n travel freely\n (0-10)",
  "Know\n women\n with loans (0-10)",
  "Know women\n who started\n activities (0-10)",
  "Know women\n travel freely \n (0-10)",
  "Prescriptive\n norms\n index",
  "No. men who think\n women shd travel\n freely (0-10)",
  "No. men who think\n women shd have\n own work (0-10)",
  "No. women who think\n women shd travel\n freely (0-10)",
  "No. women who think\n women shd have\n own work (0-10)"
  )
  
table_title = "Effects of the programs on Social norms index and components"

# Generate tables
tbl <- getTable1_mech(social_norm_index_components_vars, mainResults_mech_socialnorm, outcome_labels, table_title)

tbl
# tbl <- getTable3_het_socialnorm(social_norm_index_components_vars, mainResults_mech_socialnorm)
# tbl

```
### Private good consumption:

```{r}

outcome_labels <- c(
  "Partner private goods \n consumption (USD, yearly)",
  "Benef. private goods \n consumption (USD, yearly)",
  "Other goods consumption \n (USD, yearly)"
  )
  
table_title = "Effects of the programs on private goods consumption"

# Generate tables
tbl <- getTable1_mech(priv_expenditures, mainResults_mech_private, outcome_labels, table_title)
tbl
# Generate tables
# tbl <- getTable3_het_private(priv_expenditures, mainResults_mech_private)
# tbl


```



## Mechanism 3 : Women’s bargaining power
### Decision making

```{r}
####################### Ben
# Create a data frame of results examining heterogeneous treatment effects
# across different economic IPV outcomes, treatment variables, and heterogeneity dimensions
mainResults_mech_ben <- map_dfr(dec_making, function(depvar) {

  
    # For each treatment variable...
    tempResults2 <- map_dfr(treatment_vars, function(treat_var) {

      bind_rows(
        # Get estimates for heterogeneous treatment effects using the specified model
        getEstimate_mechanism(depvar, treat_var, control_vars, strata_vars, cluster_vars, followup_ipv_MRT_hh) %>%
          # Add columns identifying which variables were used in this iteration
          mutate(depvar = depvar, outcome = depvar, treat_var = treat_var)
        )
    })
})



outcome_labels <- c(
  "Control over \n household \n resources index",
  "Control over \n earnings \n index",
  "Own \n earnings \n influence (1-3)",
  "Can Decide \n to Earn \n Alone (1-3)",
  "Agriculture \n influence (1-3)",
  "Livestock \n influence (1-3)",
  "Off-farm \n business \n influence (1-3)",
  "Daily \n spending \n influence (1-3)",
  "Can Decide \n to Spend \n Alone (1-3)",
  "Large \n purchases \n influence (1-3)",
  "Can Decide to \n Spend Large \n Amounts Alone (1-3)",
  "Family \n planning \n influence (1-3)",
  "Can Make \n Fertility \n Choices Alone (1-3)",
  "Own \n healthcare \n influence (1-3)",
  "Can Decide \n about Self-Care \n Alone (1-3)",
  "Partner's \n earnings \n influence (1-3)",
  "Child \n education \n influence (1-3)"
  )
  
table_title = "Effects of the programs on decision making"

# Generate tables
tbl <- getTable1_mech(dec_making, mainResults_mech_ben, outcome_labels, table_title)
tbl

# tbl <- getTable4_het(dec_making, mainResults_mech_hh)
# tbl
```

### Empowerment 

```{r}

####################### Ben
# Create a data frame of results examining heterogeneous treatment effects
# across different economic IPV outcomes, treatment variables, and heterogeneity dimensions
mainResults_mech_ben <- map_dfr(empowerment, function(depvar) {

  
    # For each treatment variable...
    tempResults2 <- map_dfr(treatment_vars, function(treat_var) {

      bind_rows(
        # Get estimates for heterogeneous treatment effects using the specified model
        getEstimate_mechanism(depvar, treat_var, control_vars, strata_vars, cluster_vars, followup_ipv_MRT_hh) %>%
          # Add columns identifying which variables were used in this iteration
          mutate(depvar = depvar, outcome = depvar, treat_var = treat_var)
        )
  })
})


outcome_labels <- c(
  "Can Decide to\n Earn Alone (1-4)",
  "Wage\n earnings\n (yearly, USD)",
  "Benef. controls\n crop\n revenue (0,1)",
  "No. of\n beneficiary\n businesses",
  "Beneficiary\n has a\n business (0,1)",
  "No. of months benef worked last year",
  "Entrepreneurial\n business types\n (yearly)",
  "Beneficiary\n launched a\n business (0,1)",
  "Beneficiary\n abandoned a\n business (0,1)",
  "Personnal\n savings",
  "Business\n revenues\n (yearly, USD)",
  "Business\n profits\n (yearly, USD)",
  "Business\n asset\n value (USD)",
  "Beneficiary\n investments\n (yearly, USD)",
  "Business revenue\n (beneficiary,\n monthly, USD)",
  "Benef. owns\n livestock\n (0,1)",
  "Benef. controls\n livestock\n revenue (0,1)",
  "Benef. traveled\n for work\n (0,1)"
  )
  
table_title = "Effects of the programs on women empowerment"

# Generate tables
tbl <- getTable1_mech(empowerment, mainResults_mech_ben, outcome_labels, table_title)
tbl

# Extract results for the outcome variable 
# tbl <- getTable7_het(empowerment, mainResults_mech_ben)
# tbl
```

## Mechanism 4 : Time use
### Grouping time use variables

```{r}


####################### Ben
# Create a data frame of results examining heterogeneous treatment effects
# across different economic IPV outcomes, treatment variables, and heterogeneity dimensions
mainResults_mech_ben <- map_dfr(time_use_group, function(depvar) {
  
    # For each treatment variable...
    tempResults2 <- map_dfr(treatment_vars, function(treat_var) {

      bind_rows(
        # Get estimates for heterogeneous treatment effects using the specified model
        getEstimate_mechanism(depvar, treat_var, control_vars, strata_vars, cluster_vars, followup_ipv_MRT_hh) %>%
          # Add columns identifying which variables were used in this iteration
          mutate(depvar = depvar, outcome = depvar, treat_var = treat_var)
        )
  })
})




```

```{r}

outcome_labels <- c(
  "Tot Mins in \n household \n chores (last 7 days)",
  "Tot Mins in \n market income \n activities (last 7 days)",
  "Tot Mins in \n leisure \n activities (last 7 days)",
  "Tot Mins in \n other \n activities (last 7 days)"
  )
  
table_title = "Effects of the programs on time use"

# Generate tables
tbl <- getTable1_mech(time_use_group, mainResults_mech_ben, outcome_labels, table_title)
tbl

# Extract results for the outcome variable 
# 
# tbl <- getTable5_het(time_use_group, mainResults_mech_ben)
# tbl
```


### All variables
```{r}
####################### Ben
# Create a data frame of results examining heterogeneous treatment effects
# across different economic IPV outcomes, treatment variables, and heterogeneity dimensions
mainResults_mech_ben <- map_dfr(time_use_int, function(depvar) {
  
    # For each treatment variable...
    tempResults2 <- map_dfr(treatment_vars, function(treat_var) {

      bind_rows(
        # Get estimates for heterogeneous treatment effects using the specified model
        getEstimate_mechanism(depvar, treat_var, control_vars, strata_vars, cluster_vars, followup_ipv_MRT_hh) %>%
          # Add columns identifying which variables were used in this iteration
          mutate(depvar = depvar, outcome = depvar, treat_var = treat_var)
        )
    })
})


outcome_labels <- c(
  "Mins in \n off-farm \n business",
  "Mins spent \n retrieving \n water",
  "Mins spent \n cooking",
  "Mins spent \n agriculture",
  "Mins spent \n gathering \n firewood",
  "Mins spent \n cleaning",
  "Mins \n studying for \n Koranic school",
  "Mins spent \n doing \n laundry",
  "Mins in \n livestock",
  "Mins \n studying for \n traditional school",
  "Mins spent \n shopping",
  "Mins spent \n on childcare",
  "Mins spent \n taking care of \n disabled relatives",
  "Mins spent \n with friends",
  "Mins spent \n listening radio",
  "Mins spent \n resting",
  "Mins \n studying for \n traditional school",
  "Mins spent \n shopping",
  "Mins spent \n praying"
  )
  
table_title = "Effects of the programs on time use"

tbl <- getTable1_mech(time_use_int, mainResults_mech_ben, outcome_labels, table_title)
tbl

# Extract results for the outcome variable 
# 
# tbl <- getTable6_het(time_use_int, mainResults_mech_ben)
# tbl
```

```{r}
# remove data to free space
rm(list = ls())
```
